---
title: "Reproducible Report for Internal DFO Use Only - Protected B - Do Not Share"
subtitle: "{{u_text}}"
author: "Report generated by: {{u_name}} ({{u_email}})"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::html_document2:
    number_sections: FALSE
    theme: paper
    toc: true
    toc_depth: 5
    toc_float:
      collapsed: false
bibliography: '`r here::here("app/data/mybiblio.bib")`'
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  warning = FALSE,
  message = FALSE, 
  fig.path = "figs/")
```


```{r child = here::here("reports/sections/commonSections/commonIntro.Rmd")}
```

For more information about this report, please contact Quentin.Stoyel@dfo-mpo.gc.ca. Please circulate this report to all relevant contacts provided in each section to verify and supplement information.

# **REPRODUCIBLE REPORTING: ABOUT THIS DATA DISCOVERY TOOL** 

``` {r user-comments, results = 'asis'}
if (nchar("{{u_comments}}") > 0){
  commentSection <- "#### **Comments provided by user** \n\n
{{u_comments}}"
  writeLines(noquote(commentSection))
}
```

##### *Background*

This document compiles and summarizes regional data to increase reporting efficiency and facilitate more time-effective decision making. In response to repeat requests for available data, this report has been developed as an automated tool to document all available data within a user-defined search area. This helps streamline the process of generating science information and advice relevant to a variety of cross-sectoral departmental assessments, regulatory reviews, and reporting activities and is intended to provide information for various applications including aquaculture management, resource management, marine planning and conservation, emergency response, the Fish and Habitat Protection Program, and the Species at Risk program.

The datasets summarized in this report have been compiled from a variety of sources including internal DFO databases, governmental and academic research labs, and open-source databases. This report will be continuously updated as new sources become available. These data comprise a variety of types (e.g., points, vector datasets, raster information), with the primary focus being species presence. However, recognizing the importance of considering ecosystem-based approaches for management, this report also includes information on ecosystem components (e.g., coastal habitat), areas designated for spatial planning (e.g., Ecologically and Biologically Significant Areas), and human activities,

Data summaries and products (e.g., plots and tables) are presented in the report with source descriptions, caveats, disclaimers, sources of uncertainty, references to the literature, and contacts who can provide further interpretation. Currently, the report has the ability to report information from different sources and themes. Also, not all sections may be available in each report created as users have the ability to interactively select the modules to be included.


```{r area-map-plot, fig.height=8, fig.width=11, fig.show="hold", out.width="50%", fig.cap="Map showing the search area defined by the user (red outline) to query information and automatically generate this report (left).  Map showing the study area's location relative to the DFO Maritimes Region (right).  Dashed grey line indicates international boundries."}
graphics::par(mar = c(4, 4, .1, .1))
mapDataList$areaMap
mapDataList$regionMap

```


##### *System*

This document is developed as a reproducible reporting tool, supported by the R Markdown language, and generated by an R Shiny application interface hosted on the DFO network (http://dmapps:3838/shinySpatialApp/app/). Report summaries and outputs are based on data extracted from a user-provided search area (Figure 1). Instructions for use of the RShiny interface are provided in the repository (https://github.com/dfo-mar-odis/shinySpatialApp) and infographic (https://github.com/dfo-mar-odis/shinySpatialApp/blob/master/app/data/misc/how-to-use-reproducible-reports.pdf). Due to the potential sensitivity of some data and information, access to the data in the application has to be granted by the authoritative data provider/custodia, and the report is intended for internal DFO use only.

##### *Disclaimers*

This report is intended to provide a first-order view of the data available within the search area. Users are requested to review the caveats and disclaimers below to use information appropriately.

- This document is a tool to support, not to replace, Science advice and peer-review processes.
- This report does not endeavor to describe every source of information available; the data presented does not represent all available data within the search area and additional information may be available from other sources, or more recent data may be available than what is presented here.
- This report is not intended to provide the data itself, but to summarize what is available. Users are encouraged to:
  - Access the original data source if more information is required,
  - Circulate this document to all contacts outlined in the different sections of the report for each data source, to ensure the veracity of inference drawn from the report, and to provide any supplemental information that may support the provision of science advice.
- Data and metadata summarized in this report may change frequently because different sources of information may change, or may get updated, without prior notice. Consequently, reports may summarize different outputs of the same polygon depending on their date of creation. 
-	The focus of this report is on available observations of species presence and not on absences, quantities (e.g., species abundance or biomass), frequency, or catch information.
-	The absence of a species in this report should be interpreted as an absence of observation or reporting of the species within the user-defined search area, not necessarily as a true absence of the species.
-	Unless otherwise specified, data were queried from 2010 to present. This was selected as an arbitrary time range to present the most recent information. Please contact data providers if data outside of these ranges are required.
-	Current outputs of species observations in the report aggregate all years in summary plots and tables (e.g. 2010-2021). Annual summaries are not displayed. If you require annual summaries or other information beyond species presence, please contact relevant data providers/custodians for each data source.
-	All maps in this report are for informational purposes and are not suitable for legal or surveying purposes. Maps represent only the approximate location of boundaries.
-	This report is intended for internal DFO use only. Privacy screening (i.e., the rule of 5) is not yet integrated into all data products and summaries generated by the report.
-	Outputs of this report are not suitable for real-time, dynamic spatial planning.
-	Because coastal areas of the Scotian Shelf bioregion are generally not adequately sampled to characterize fine-scale ecological characteristics (i.e., species, habitat composition and variability within a sub-regional focal area), the distribution of (some) species featured within the report, when the search area is near to the coast, should be used as a first-order estimate limited by the spatial-temporal resolution of available data.

##### *Data Access & Quality Tiers*

This report incorporates information from a variety of sources with differing levels of accessibility and quality control. Consequently, data sources in the report are categorized based on data access considerations, tiers of data quality, and associated usage recommendations.

Security level considerations for data access are divided in three categories:

- Open Data: Data open to the public available in the public facing platform for spatial data within the Open Government Portal https://open.canada.ca/en/open-data
- Secure Data: Data products that are in the process of being published in Open Data, and/or data products that are available upon request to data providers/custodians, and not suitable for publication in open data.
- Protected B Data: Applies to information or assets that, if compromised, could cause serious injury to an individual, organization or government. https://www.tpsgc-pwgsc.gc.ca/esc-src/protection-safeguarding/niveaux-levels-eng.html

Tiers of data quality were developed by the report generators and data providers in order to provide guidance and urge caution when interpreting the data summaries. Note subjectivity remains in this classification; we welcome suggestions about how to improve this section to characterize information from a vast variety of sources.

```{r table-tiers-read, echo=FALSE, cache=FALSE, include = FALSE}
table_tier <- read.csv(here::here("app/data/misc/table_tiers_EN.csv"))
```

```{r tier-table}
knitr::kable(table_tier,align="l",
      caption = "Quality tiers defined to describe sources of information queried and summarized in this report.", booktabs = T, escape = F, linesep="") %>% kableExtra::kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
```


<!-- MAIN SECTIONS -->

# **DATA DISCOVERY OUTPUTS**  
{{add_parts}}

<!-- GENERIC END -->

## **REGIONAL SYNTHESIS**

This section provides an overall synthesis of regional data and data products of human activities and species contained within the search area. This summary must be used in coordination with all the information presented throughout the report, including the descriptions, caveats, disclaimers, sources of uncertainty, references to the literature, and contacts who can provide further interpretation. This section is not intended to provide the data itself, but to summarize what is available. Users are encouraged to access the original data source if more information is required.

### **Multi-Threat Synthesis**

This section summarizes available information of human activities and human threats in the search area, as well as relevant information relevant for species listed by SARA, and/or assessed by COSEWIC. Outputs are not suitable for real-time, dynamic spatial planning.

#### *Interactive Output*

This section summarizes available information of human activities in the search area, per each data source presented in this report. Please contact data providers if data outside of these ranges are required. Outputs are not suitable for real-time, dynamic spatial planning.

### **Multi-Species Synthesis**

This section summarizes available information of presence of species in the search area listed by SARA, and/or assessed by COSEWIC, per each data source presented in this report. The absence of a species in this report should be interpreted as an absence of observation or reporting of the species within the search area, not necessarily as a true absence of the species. Unless otherwise specified, data were queried from 2010 to present. Please contact data providers if data outside of these ranges are required. Outputs are not suitable for real-time, dynamic spatial planning.

```{r sar-obs-summary-table}
absentCode <- "&nbsp;-&nbsp;"
presentCode <- "&#x2714;"
summarySarTable[is.na(summarySarTable)] <- absentCode
formatedSarTable <-dplyr:: mutate_all(summarySarTable, ~ kableExtra::cell_spec(., color = ifelse(. == presentCode, "white", ""), background = ifelse(. == presentCode, "green", ""), escape = FALSE))

```

```{r sar-hab-summary-table}
  summaryHabTable[is.na(summaryHabTable)] <- "&nbsp;-&nbsp;"

  # add column for observations from sar table
  obsColumn <- apply(summarySarTable, 1, function(r) any(r %in% c(presentCode)))
  summaryHabTable$Obs <- ifelse(obsColumn, presentCode, absentCode)

  summaryHabTable <- dplyr::mutate_all(summaryHabTable, ~ kableExtra::cell_spec(., color = ifelse(. == presentCode, "white", ""),
                  background = ifelse(. == presentCode, "green", ""), escape = FALSE))

  names(summaryHabTable) <- c("Species", "COSEWIC", "SARA", "Observations", "SAR Range", "SDM", "Important Habitat", "Critical Habitat")


```

```{r output-hab-table}
knitr::kable(summaryHabTable, align="l", caption = "Regional synthesis of data and data products of species contained within the search area that are listed by the Species At Risk Act (SARA), and/or assessed by the Committee on the Status of Endangered Wildlife in Canada (COSEWIC). Data points (observations) are summarized in more detail in the subsequent table. A description of the different sources of information for Species at Risk is available in the infographic: https://github.com/dfo-mar-odis/shinySpatialApp/blob/master/app/data/misc/SAR-information-type-reproducible-reports.pdf). The absence of a species in this table should be interpreted as an absence of reporting, not necessarily as an absence of the species in the area. Outputs are not suitable for real-time, dynamic spatial planning.", booktabs = T, escape = F, linesep = "") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
```

```{r output-sar-table}
knitr::kable(formatedSarTable, align="l", caption = "Summary of regional data points (observations) of species contained within the search area that are listed by the Species At Risk Act (SARA), and/or assessed by the Committee on the Status of Endangered Wildlife in Canada (COSEWIC). Presence of a species in at least one of these data sources is reported as a presence in the data points (observations) in the table above. The absence of a species in this table should be interpreted as an absence of reporting, not necessarily as an absence of the species in the area. Outputs are not suitable for real-time, dynamic spatial planning.", booktabs = T, escape = F, linesep = "") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
```

# **CONTRIBUTORS**
```{r read-contributors, echo=FALSE, cache=FALSE, include = FALSE, results='asis'}
people <- read.csv(here::here("app/data/misc/contributors.csv"),  encoding="UTF-8")
people <- people$list
sort(people)
```
List of contributors (listed in alphabetical order) that have contributed with with data, context, and ideas for the reproducible reporting initiative: `r knitr::combine_words(people)`.

# **REFERENCES**    

<!-- APPENDIX -->
{{add_appendix}}


# **SUPPLEMENTARY MATERIAL 1: Context about the Ocean Biodiversity Information System (OBIS), the Global Biodiversity Information Facility (GBIF), and iNaturalist**

Note this section is only relevant if the species modules are rendered as part of the Reproducible Report.

Both OBIS and GBIF are large online data portals, consisting of numerous datasets from multiple sources. Due to their many commonalities, the following descriptions and caveats are applicable to both and therefore written together.

### **Data structure**

Data submitted to GBIF and OBIS must be formatted according to the
Darwin Core, a body of standards outlining how to format biological data
(<https://obis.org/manual/darwincore/> and
<https://www.gbif.org/darwin-core>). These standards define which
attributes (i.e., column names) are included when structuring the
datasets, and describe how other supplemental information such as study
design, associated environmental conditions (e.g., sea surface
temperature), or biological characteristics (e.g., abundance, biomass,
etc.) can be formatted and included. Due to these requirements, OBIS and
GBIF are generally best suited for point data, although other vector
formats (e.g., lines, polygons) can be uploaded. Because this report
focuses on species presence, detailed information outlining the study
design, environmental conditions, or biological characteristics are not
included, but may be available for each dataset if required.

OBIS and GBIF submissions also follow the Ecological Metadata Language
format, a metadata standard for ecological data (more information here:
<https://obis.org/manual/eml/>). This is created as an XML file for each dataset.

For more detailed metadata including information such as the data
collection date, survey methods, institution name, and license type,
refer to the provided URL for each dataset.

### **Disclaimers**

There are various issues involved with using data extracted from OBIS
and GBIF, which are described below in more detail. Future iterations of this reporting tool will aim at expanding our quality checks to address these concerns. Because these portals contain data from many different sources, this is not an exhaustive list of all of the potential caveats of each data source. Users should refer to each source separately to review these concerns.

### **Differing research objectives**

Each dataset within these portals was acquired to fulfill its own unique
research objectives, and therefore may not be suitable for all
applications. When data are viewed spatially, other factors that can
affect the results including the study design, data collection methods,
and collection date may not be immediately apparent. In particular, the
absence of a species should be interpreted as an absence of reporting,
not necessarily as an absence of the species in the area.

### **Observations over land**

Although this report focuses on marine biodiversity data, observations
on land for the species of interest are often uploaded to these portals.
Several aquatic species have life history strategies involving presence
within freshwater ecosystems, rather than existing solely within marine
or oceanic ecosystems (e.g., anadromous fish). Observations appearing
"on land" may therefore represent species observed within freshwater
ecosystems such as rivers or ponds, which may not be obvious in the
Figures shown. Fish and invertebrate species occurring on land were
therefore not removed from the report. Cetaceans observations on land
typically indicate that animals were sighted from shore. Any
observations \>300 m from the shore were removed due to positional
accuracy and species identification concerns. Because geopositional
errors are known to occur within these portals, users should
double-check observations occurring on land to ensure they contain
accurate information.

OBIS performs multiple data quality checks, including flagging data over land. For a complete description of the QC procedures OBIS performs, see
<https://github.com/iobis/obis-qc> and Vandepitte et al. (2015). Data
quality checks are less extensive in GBIF, various information is
required (e.g., scientific name, event date) or the records will not be
accepted (<https://www.gbif.org/data-quality-requirements-occurrences>).

### **Duplicate datasets**

Several of the datasets uploaded to OBIS and GBIF are also listed as
separate data sources/sections within this report. These have been
removed from this section of the report and include:

-   Maritimes Research Vessel Surveys

-   Whale Sightings Database (named "DFO Maritimes Region Cetacean
    Sightings" in OBIS and GBIF)

Duplicates datasets and occurrence records may also exist between OBIS
and GBIF. Data contributors are encouraged to upload to both portals
simultaneously, although in some instances, data is only uploaded to one
portal, which can lead to discrepancies between the two. Also, records
are often shared between multiple data contributors, and as a result,
some records may be included in several different datasets. Currently, R
tools are being developed to address these data duplicate issues
(<https://www.rdocumentation.org/packages/spoccutils/versions/0.1.0/topics/spocc_duplicates>).
These tools may be incorporated in future iterations of this report when
they become available.

### **Additional data**

In some cases, data uploaded to OBIS or GBIF may not represent the
entire dataset available. Users should review the URLs for each dataset
to identify these instances and contact the original data providers if
there are additional records that may be useful.

### **Basis of Record**

The Basis of Record field (i.e., column name) is a required term that specifies the nature of
the record, such as how the observation was obtained or stored (more
information here: <https://obis.org/manual/darwincore/#records>). There
are various options the data submitter can select from. The following
cases were removed from the report because they do not contain relevant
or current specimen data:

-   FossilSpecimen: specimen is a fossil record.

-   LivingSpecimen: specimen is intentionally kept or cultivated such as
    a culture organism, zoo or aquarium species.

The following cases provide relevant information and were combined
within the report:

-   MaterialSample: A physical sample from the sampling event has been
    retained. The recorded location is the in situ sampling location.

-   PreservedSpecimen: organism is collected at the recorded location
    but then preserved (e.g., in ethanol at a location such as museum,
    university, or research institute.)

-   HumanObservation: includes visual sightings of the organism, or
    observations where specimens were collected and then discarded after
    counting (e.g., a benthic grab sample).

-   Unknown: includes records without a defined basis of record or with
    an unrecognized value for this field

Observations may also be listed as MachineObservation, which are derived from machine or computer-based detections such as automated sensors (e.g., DNA sequencers), acoustic tagging, or image recognition. Currently, there are no MachineObservation records for fish or invertebrate species in this region.

### **iNaturalist data**

iNaturalist is an open-source platform where naturalists, citizen
scientists, and biologists can map species observations [@iNaturalist]. As of April 2022, iNaturalist has over 95 million species
observations and over 2.1 million registered users/contributors
globally. Every week, iNaturalist data that are considered "Research
Grade" (i.e., the record contains a date, is georeferenced, has photos
or sounds, isn't a captive or cultivated organism, and two thirds of
identifiers agree on the species identification) are added to GBIF (more
information here:
<https://www.gbif.org/dataset/50c9509d-22c7-4a22-a47d-8c48425ef4a7>).
iNaturalist records are not added to OBIS.

iNaturalist records include a coordinate uncertainty, which is added by
the user to provide an estimation of the geopositional accuracy of the
observation. This may reflect information such as the accuracy of the
user's phone's GPS, or an estimation of error if an observation was
spotted from a distance
(<https://greece.inaturalist.org/posts/28376-making-yourobservations-more-valuable-for-conservation-location-uncertainty>).

For species that may be put at risk if their true location is known
(e.g., due to hunting or poaching), the location can be obscured, either
at the request of the submitter, or done automatically by iNaturalist.
iNaturalist moderators may obscure a species location if the species has
a certain conservation status (e.g., the IUCN equivalent of "Near
Threatened" or worse), or based on local knowledge of the species in the
region (<https://www.inaturalist.org/pages/curator+guide>). For species
with obscured locations, a random location within a 0.2 x 0.2 degree
cell (\~22 km x 22 km) is generated
(<https://www.inaturalist.org/pages/help#geoprivacy>). In GBIF, it is
not explicitly stated if the species position has been obscured, but can
implied if the coordinate uncertainty is \~22 km.

Due to these issues with the coordinate uncertainty, occurrence records
from iNaturalist data are listed separately within the GBIF data
section, and the associated coordinate uncertainty is provided.

### **Data searches**

OBIS and GBIF records included in this section were extracted using the
robis (Provoost & Bosch, 2021) and rgbif (Chamberlain et al., 2021) R
packages, respectively. Data in this report were compiled for fish and
invertebrate species that have been listed by SARA, and/or assessed by
COSEWIC within the user-defined search area. The code used for these
searches can be found here:
<https://github.com/dfo-mar-odis/shinySpatialApp>.


