---
output:
  bookdown::html_document2:
    number_sections: FALSE
    theme: paper
bibliography: '`r here::here("app/data/mybiblio.bib")`'
editor_options: 
  markdown: 
    wrap: 72
---

### **Ocean Biodiversity Information System (OBIS)**{#OBIS-section}

```{r obis-load, include=FALSE}
# prevent future common obis sections from running
obisEnv$commonObis <- FALSE
load_rdata(c("obisFish_rr"), regionStr, env = environment())
```

```{r obis-meta, results='asis'}
write_meta(obisFish_rr, "EN")
```

OBIS is a global, open-access data and information clearing-house on marine biodiversity for science, conservation, and sustainable development [@OBIS]. Their vision is to build and maintain a global alliance that collaborates with scientific communities to facilitate free and open-access to, and application of, biodiversity and biogeographic data and information on marine life. OBIS accepts data from any organization, consortium, project or individual who wishes to contribute data (OBIS, 2021). As of December 2021, OBIS has over 80 million species occurrence records and over 4,300 datasets globally.


### **Global Biodiversity Information Facility (GBIF)** {#gbif-section}

```{r gbif-load, include=FALSE}
load_rdata(c("gbifFish_rr"), regionStr, env = environment())
```

```{r gbif-meta, results='asis'}
write_meta(gbifFish_rr, "EN")
```

GBIF is an international network and data infrastructure funded by the world's governments and aimed at providing anyone, anywhere, open access to data about all types of life on Earth (GBIF, 2021). Similar to OBIS, GBIF accepts data from various contributors such as university laboratories, government departments or private research institutions, although GBIF accepts both marine and terrestrial species data. As of December 2021, GBIF has over 1.9 billion species occurrence records and over 63,000 datasets globally. 



### Background descriptions for both OBIS and GBIF

Both OBIS and GBIF are large online data portals, consisting of numerous
datasets from multiple sources. Due to their many commonalities, the
following descriptions and caveats are applicable to both and therefore
written together.

#### Data structure

Data submitted to GBIF and OBIS must be formatted according to the
Darwin Core, a body of standards outlining how to format biological data
(<https://obis.org/manual/darwincore/> and
<https://www.gbif.org/darwin-core>). These standards define which
attributes (i.e., column names) are included when structuring the
datasets, and describe how other supplemental information such as study
design, associated environmental conditions (e.g., sea surface
temperature), or biological characteristics (e.g., abundance, biomass,
etc.) can be formatted and included. Due to these requirements, OBIS and
GBIF are generally best suited for point data, although other vector
formats (e.g., lines, polygons) can be uploaded. Because this report
focuses on species presence, detailed information outlining the study
design, environmental conditions, or biological characteristics are not
included, but may be available for each dataset if required.

OBIS and GBIF submissions also follow the Ecological Metadata Language
format, a metadata standard for ecological data (more information here:
<https://obis.org/manual/eml/>). This is created as an XML file for each
dataset.

For more detailed metadata including information such as the data
collection date, survey methods, institution name, and license type,
refer to the provided URL for each dataset.

#### Disclaimers

There are various issues involved with using data extracted from OBIS
and GBIF, which are described below in more detail. Future iterations of
this reporting tool will aim at expanding our quality checks to address
these concerns. Because these portals contain data from many different
sources, this is not an exhaustive list of all of the potential caveats
of each data source. Users should refer to each source separately to
review these concerns.

#### Differing research objectives

Each dataset within these portals was acquired to fulfill its own unique
research objectives, and therefore may not be suitable for all
applications. When data are viewed spatially, other factors that can
affect the results including the study design, data collection methods,
and collection date may not be immediately apparent. In particular, the
absence of a species should be interpreted as an absence of reporting,
not necessarily as an absence of the species in the area.

#### Observations over land

Although this report focuses on marine biodiversity data, observations
on land for the species of interest are often uploaded to these portals.
Several aquatic species have life history strategies involving presence
within freshwater ecosystems, rather than existing solely within marine
or oceanic ecosystems (e.g., anadromous fish). Observations appearing
"on land" may therefore represent species observed within freshwater
ecosystems such as rivers or ponds, which may not be obvious in the
Figures shown. Fish and invertebrate species occurring on land were
therefore not removed from the report. Cetaceans observations on land
typically indicate that animals were sighted from shore. Any
observations \>300 m from the shore were removed due to positional
accuracy and species identification concerns. Because geopositional
errors are known to occur within these portals, users should
double-check observations occurring on land to ensure they contain
accurate information.

OBIS performs multiple data quality checks, including flagging data over
land. For a complete description of the QC procedures OBIS performs, see
<https://github.com/iobis/obis-qc> and Vandepitte et al. (2015). Data
quality checks are less extensive in GBIF, various information is
required (e.g., scientific name, event date) or the records will not be
accepted (<https://www.gbif.org/data-quality-requirements-occurrences>).

#### Duplicate datasets

Several of the datasets uploaded to OBIS and GBIF are also listed as
separate data sources/sections within this report. These have been
removed from this section of the report and include:

-   Maritimes Research Vessel Surveys

-   Whale Sightings Database (named "DFO Maritimes Region Cetacean
    Sightings" in OBIS and GBIF)

Duplicates datasets and occurrence records may also exist between OBIS
and GBIF. Data contributors are encouraged to upload to both portals
simultaneously, although in some instances, data is only uploaded to one
portal, which can lead to discrepancies between the two. Also, records
are often shared between multiple data contributors, and as a result,
some records may be included in several different datasets. Currently, R
tools are being developed to address these data duplicate issues
(<https://www.rdocumentation.org/packages/spoccutils/versions/0.1.0/topics/spocc_duplicates>).
These tools may be incorporated in future iterations of this report when
they become available.

#### Additional data

In some cases, data uploaded to OBIS or GBIF may not represent the
entire dataset available. Users should review the URLs for each dataset
to identify these instances and contact the original data providers if
there are additional records that may be useful.

#### Basis of Record

The Basis of Record field (i.e., column name) is a required term that specifies the nature of
the record, such as how the observation was obtained or stored (more
information here: <https://obis.org/manual/darwincore/#records>). There
are various options the data submitter can select from. The following
cases were removed from the report because they do not contain relevant
or current specimen data:

-   FossilSpecimen: specimen is a fossil record.

-   LivingSpecimen: specimen is intentionally kept or cultivated such as
    a culture organism, zoo or aquarium species.

The following cases provide relevant information and were combined
within the report:

-   MaterialSample: A physical sample from the sampling event has been
    retained. The recorded location is the in situ sampling location.

-   PreservedSpecimen: organism is collected at the recorded location
    but then preserved (e.g., in ethanol at a location such as museum,
    university, or research institute.)

-   HumanObservation: includes visual sightings of the organism, or
    observations where specimens were collected and then discarded after
    counting (e.g., a benthic grab sample).

-   Unknown: includes records without a defined basis of record or with
    an unrecognized value for this field

Observations may also be listed as MachineObservation, which are derived from machine or computer-based detections such as automated sensors (e.g., DNA sequencers), acoustic tagging, or image recognition. Currently, there are no MachineObservation records for fish or invertebrate species in this region.

#### iNaturalist data

iNaturalist is an open-source platform where naturalists, citizen
scientists, and biologists can map species observations (iNaturalist,
2021). As of December 2021, iNaturalist has over 86 million species
observations and over 1.9 million registered users/contributors
globally. Every week, iNaturalist data that are considered "Research
Grade" (i.e., the record contains a date, is georeferenced, has photos
or sounds, isn't a captive or cultivated organism, and two thirds of
identifiers agree on the species identification) are added to GBIF (more
information here:
<https://www.gbif.org/dataset/50c9509d-22c7-4a22-a47d-8c48425ef4a7>).
iNaturalist records are not added to OBIS.

iNaturalist records include a coordinate uncertainty, which is added by
the user to provide an estimation of the geopositional accuracy of the
observation. This may reflect information such as the accuracy of the
user's phone's GPS, or an estimation of error if an observation was
spotted from a distance
(<https://greece.inaturalist.org/posts/28376-making-yourobservations-more-valuable-for-conservation-location-uncertainty>).

For species that may be put at risk if their true location is known
(e.g., due to hunting or poaching), the location can be obscured, either
at the request of the submitter, or done automatically by iNaturalist.
iNaturalist moderators may obscure a species location if the species has
a certain conservation status (e.g., the IUCN equivalent of "Near
Threatened" or worse), or based on local knowledge of the species in the
region (<https://www.inaturalist.org/pages/curator+guide>). For species
with obscured locations, a random location within a 0.2 x 0.2 degree
cell (\~22 km x 22 km) is generated
(<https://www.inaturalist.org/pages/help#geoprivacy>). In GBIF, it is
not explicitly stated if the species position has been obscured, but can
implied if the coordinate uncertainty is \~22 km.

Due to these issues with the coordinate uncertainty, occurrence records
from iNaturalist data are listed separately within the GBIF data
section, and the associated coordinate uncertainty is provided.

#### Data searches

OBIS and GBIF records included in this section were extracted using the
robis (Provoost & Bosch, 2021) and rgbif (Chamberlain et al., 2021) R
packages, respectively. Data in this report were compiled for fish and
invertebrate species that have been listed by SARA, and/or assessed by
COSEWIC within the user-defined search area. The code used for these
searches can be found here:
<https://github.com/dfo-mar-odis/shinySpatialApp>.
