---
title: "Reproducible Report for internal DFO use only: DRAFT"
subtitle: {{u_text}}
author: "Report generated by: {{u_name}} ({{u_email}})"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::html_document2:
    number_sections: FALSE
    theme: paper
    toc: true
    toc_depth: 5
  pdf_document:
    toc: true
  word_document:
    toc: true
bibliography: ../data/mybiblio.bib
---

<style>
table {background-color: white !important;color: black !important;}
caption {color: black !important;}
a:link {color: #002080;}
a:visited {color: #008040;}
a:hover {color: #006080;}
</style>

```{r setup and libraries, echo=FALSE, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, fig.align="left")
```

```{r load data and functions, echo=FALSE, include=FALSE, cache=FALSE}
minYear <- 2010
load("../data/OpenData.RData")
load("../data/OpenData_sardist.RData")
load("../data/SecureData.RData")
#load("\\\\ent.dfo-mpo.ca\\ATLShares\\Science\\BIODataSvc\\SRC\\Reproducible_Reporting\\data\\SecureData.Rdata")
lapply(list.files("../R", pattern = ".[Rr]$", full.names = TRUE),source) # check helpers.R for a list of packages
```

```{r Search Area and setup.R, echo=FALSE, include=FALSE, cache=FALSE}
 studyArea <- sf::st_read("{{path_to_geoms}}")
# studyArea <- sf::st_read("geoms_slc.geojson")
# Uncomment the following to test fixed polygon:
# studyArea <- st_read("../studyAreaTest/geoms_slc_test.geojson")#Offshore
# studyArea <- st_read("../studyAreaTest/geoms_slc_coastal_test.geojson")#coastal 
# studyArea <- st_read("../studyAreaTest/geoms_slc_no_land.geojson") #no land
Region <- st_read("../studyAreaTest/geoms_slc_MarBioRegion.geojson")
site <- sf::st_centroid(studyArea) 
```
 
```{r parameters for area_map.r, echo=FALSE, include=FALSE, cache=FALSE}
# The following defines studyBox geometry "look". studyBox_geom is input into area map or can be added to any map later
studyBox_geom <- geom_sf(data=studyArea, fill=NA, col="red", size=1) 

# The following plots area map using function (output is a list)
areaMapList<-area_map(studyArea, site, land50k_sf, 5, bounds_sf, studyBox_geom)

# The following separates items in the output list: first item is a map and second is a bounding box of the map
areaMap=areaMapList[[1]] # map
bboxMap=areaMapList[[2]] #bounding box of the map
```

```{r parameters for region_map.r, echo=FALSE, include=FALSE, cache=FALSE}
# Bounding box for the region
regionBox <- sf::st_bbox(Region) 

# Create the regional map
regionMap <- region_map(regionBox, studyArea, land10m_sf, bounds_sf)  
```

<!-- # ```{r child = c('../Rmd/report_cetaceans_EN.Rmd', 'report_fish_EN.Rmd', 'report_habitat_EN.Rmd', 'report_planning_EN.Rmd', 'report_SARA_EN.Rmd')} -->
<!-- # ``` -->
 <!-- ```{r child = '../Rmd/report_SARA_EN.Rmd'} -->
 <!-- ``` -->

<!-- END  -->

<!-- MAIN SECTIONS -->

# **REPRODUCIBLE REPORTING**  

#### **Comments provided by user** 

{{u_comments}}

#### **About this report**

This document summarizes regional data available at the time of report creation, including information on species and habitats. Data summaries and products (e.g., plots and tables) are presented with source descriptions, caveats, disclaimers, sources of uncertainty, references to the literature, and contacts who can provide further interpretation. This report streamlines the process of generating science information and advice relevant to a variety of cross-sectoral departmental assessments, regulatory reviews, and reporting activities.

This document is developed as a reproducible reporting tool, supported by the R markdown language and generated by an R-Shiny application interface hosted on the DFO network. Report summaries and outputs are based on data extracted from a user-provided search area (a focal polygon of interest) with a user-defined buffer (Figure 1). Instructions for use of the R-Shiny interface are provided in the technical manual. Due to the potential sensitivity of some data and information, access to the data in the application has to be granted, and the report is intended for internal use only. 

````{r, fig.height=8, fig.width=11, fig.cap='Map showing the search area defined by the user (outlined in red) to query information and automatically generate this report. '}
areaMap
# areaMap can be plotted once and then reused for other plots
```

The output from the search includes the following sections: 
1) Information from the National Aquatic Species at Risk Geodatabase,
2) Fish and Invertebrates,
3) Cetaceans,
4) Habitat,
5) Areas designated for spatial planning.

#### **How to use this report?**  

- This document is a tool to support, not to replace, Science advice.
-	This document must be circulated to all contacts (provided in the report) for each data source to ensure the veracity of inference drawn from the report, and to provide any supplemental information that may support the provision of science advice. Users can also request additional data and/or metadata directly from each contact. 
-	The focus of this report is on species presence: 
  - This report summarizes available observations of species presence (**primarily since 2010**) and not on absences, quantities (e.g., species abundance or biomass), frequency, or catch information.
  - Current outputs of species observations in the report aggregate all years in summary plots and tables (e.g. 2010-2021). Annual summaries are not displayed. 
  - If you require annual summaries or other information beyond species presence, please inform relevant contacts for each data source.
- All maps in this report are for informational purposes and are not suitable for legal or surveying purposes. Maps represent only the approximate location of boundaries.
-	This report is intended for internal DFO use only. Privacy screening (i.e., the rule of 5) is not yet integrated into all data products and summaries generated by the report.
-	The absence of a species in this report should be interpreted as an absence of observation or reporting of the species in the focal area, not necessarily as a true absence of the species. 
-	The focus of this report is on available observations of species presence and not on absences, quantities (e.g., species abundance or biomass), frequency, or catch information. 
-	Because coastal areas of the Scotian Shelf bioregion are generally not adequately sampled to characterize fine-scale ecological characteristics (i.e., species, habitat composition and variability within a sub-regional focal area), the distribution of (some) species featured within the report, when the focal area is near to the coast, should be used as a first-order estimate limited by the spatial-temporal resolution of available data.

This report incorporates information from a variety of sources with differing levels of quality control. Consequently, data sources in the report are categorized into tiers of data quality, and associated usage recommendations.

```{r table tiers read, echo=FALSE, cache=FALSE, include = FALSE}
table_tier <- read.csv("../data/misc/table_tiers_EN.csv")
```
```{r}
knitr::kable(table_tier,align="l", 
      caption = "Quality Tiers defined to describe sources of information queried and summarized in this report.", booktabs = T, escape = F, linesep="") %>% kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
```

# **SEARCH RESULTS**  

Aquatic Species that have been listed under the _Species At Risk Act_ (SARA) or assessed by the Committee on the Status of Endangered Wildlife in Canada (COSEWIC) are the current focus of this reproducible reporting framework. Recognizing the importance of considering ecosystem-based approaches for management, this report also includes information on other species (e.g., commercial, recreational, ecologically significant), ecosystem components (e.g., coastal habitat), and areas designated for spatial planning (e.g., Ecologically and Biologically Significant Areas) for each user-defined area.

The following are definitions relevant for species listed by the _Species at Risk Act_ (SARA) or assessed by the Committee on the Status of Endangered Wildlife in Canada (COSEWIC). Note: COSEWIC species assessed as Special Concern, Threatened, and Endangered may be listed by SARA.

- **SARA** - The following text was obtained from the SARA website (URL below). The _Species at Risk Act_ (SARA) was proclaimed in June 2003; it is one part of a three part Government of Canada strategy for the protection of wildlife Species At Risk. This three part strategy also includes commitments under the Accord for the Protection of Species At Risk and activities under the Habitat Stewardship Program for Species At Risk. The purposes of SARA are to prevent Canadian indigenous species, subspecies, and distinct populations from becoming extirpated or extinct, to provide for the recovery of endangered or threatened species, and encourage the management of other species to prevent them from becoming at risk. It applies to all federal lands in Canada; all wildlife species listed as being at risk; and their critical habitat. For more information on SARA visit <https://www.canada.ca/en/environment-climate-change/services/species-risk-public-registry.html> 

- **COSEWIC** - The following text was obtained from the COSEWIC website (URL below): The Committee on the Status of Endangered Wildlife in Canada (COSEWIC) is an independent advisory panel to the Minister of Environment and Climate Change Canada that meets twice a year to assess the status of wildlife Species At Risk of extinction. Members are wildlife biology experts from academia, government, non-governmental organizations and the private sector responsible for designating wildlife species in danger of disappearing from Canada. COSEWIC determines the national status of wild Canadian species, subspecies, varieties or other designatable units that are suspected of being at risk of extinction or extirpation. COSEWIC uses a process based on science and Aboriginal or community knowledge to assess wildlife Species At Risk. All native mammals, birds, reptiles, amphibians, fish, arthropods, molluscs, vascular plants, mosses and lichens are included in COSEWIC's current mandate. For more information on COSEWIC visit <https://www.cosewic.ca/index.php/en-ca/>

{{add_main_sections}}

<!-- HABITAT -->

{{add_appendix}}

<!-- EBSA -->

{{add_ebsa_section}}

<!-- GENERIC END -->

# **CONTRIBUTORS**
```{r read contributors, echo=FALSE, cache=FALSE, include = FALSE}
people <- read.csv("../data/misc/contributors.csv")
people <- people$list
sort(people)
```
List of contributors (listed in alphabetical order): `r knitr::combine_words(people)`. 

For more information about this report, please contact Tana.Worcester@dfo-mpo.gc.ca

# **REFERENCES**    





