---
title: "Reproducible Report for internal DFO use only: DRAFT"
subtitle: {{u_text}}
author: "Report generated by: {{u_name}} ({{u_email}})"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::html_document2:
    number_sections: FALSE
    theme: paper
    toc: true
    toc_depth: 5
  pdf_document:
    toc: true
  word_document:
    toc: true
bibliography: ../data/mybiblio.bib
---

<style>
table {background-color: white !important;color: black !important;}
caption {color: black !important;}
a:link {color: #002080;}
a:visited {color: #008040;}
a:hover {color: #006080;}
</style>

```{r setup and libraries, echo=FALSE, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, fig.align="left")
# check helpers.R for a list of packages
```

```{r load data and functions, echo=FALSE, include=FALSE, cache=FALSE}
minYear <- 2002
load("../data/OpenData.RData")
load("../data/OpenData_sardist.RData")
load("../data/SecureData.RData")
#load("\\\\ent.dfo-mpo.ca\\ATLShares\\Science\\BIODataSvc\\SRC\\Reproducible_Reporting\\data\\SecureData.Rdata")
load("../data/MARFISSCI.SPECIES.RData")
ISDB_info<-file.info("../data/ISDB.ISSETTYPECODES.RData")
MARFIS_info<-file.info("../data/MARFISSCI.SPECIES.RData")
lapply(list.files("../R", pattern = ".[Rr]$", full.names = TRUE),source)
```

```{r Search Area and setup.R, echo=FALSE, include=FALSE, cache=FALSE}
#studyArea <- st_read("{{path_to_geoms}}")
#studyArea <- st_read("geoms_slc.geojson")
# Uncomment the following to Test Outside the App:
#studyArea <- st_read("../Rmd/geoms_slc_test.geojson")#Offshore
#studyArea <- st_read("../Rmd/geoms_slc_coastal_test.geojson")#coastal 
studyArea <- st_read("../Rmd/geoms_slc_no_land.geojson")#no land
site <- sf::st_centroid(studyArea)  
lapply(list.files("../Rmd", pattern = ".[Rr]$", full.names = TRUE),source)
lapply(list.files("../R", pattern = ".[Rr]$", full.names = TRUE),source)
```

#```{r child = c('../Rmd/report_cetaceans_EN.Rmd', 'report_fish_EN.Rmd', #'report_habitat_EN.Rmd', 'report_SARA_EN.Rmd')}
#```

```{r child = '../Rmd/report_habitat_EN.Rmd'}
```

<!-- END  -->

<!-- MAIN SECTIONS -->

# **REPRODUCIBLE REPORTING**  

#### **Comments provided by user** 

{{u_comments}}

#### **About this report**

This document summarizes regional data, including information on species and habitats, available at the time of report creation. Data summaries and products (e.g., plots and tables) are presented with source descriptions, caveats, disclaimers, sources of uncertainty, references to the literature, and contacts of relevant staff who can provide further interpretation. This report streamlines the process of generating science information and advice relevant to a variety of cross-sectoral departmental assessments, regulatory reviews, and reporting activities.

This document is developed as a reproducible reporting tool, supported by the R markdown language and generated by an R-Shiny application interface hosted on the DFO network. Report summaries and outputs are based on data extracted from a user-provided search area (a focal polygon of interest) with a user-defined buffer (Figure 1). Instructions for use of the R-Shiny interface are provided in the technical manual. Due to the potential sensitivity of some data and information, access to the data in the application has to be granted, and the report is intended for internal use only. 

````{r Fig 1 search polygon, fig.height=8, fig.width=11, fig.cap='Map showing the search area defined by the user: location of the proposed project/activity is highlighted in yellow (input polygon), surrounded by an exposure zone or user-defined buffer area in blue. Buffer area is used by this tool to query information and automatically generate a report. '}
#note setup.R has a few lines to get the following line working
areaMap
# areaMap can be plotted once and then reused for other plots
```
Species that have been listed by the _Species At Risk Act_ (SARA), assessed by the Committee on the Status of Endangered Wildlife in Canada (COSEWIC), or included in the Wild Species listings, are the current focus of this reproducible reporting framework. Recognizing the importance of considering ecosystem-based approaches for management, this report also includes information on other (e.g., commercial, recreational, ecologically significant) species, ecosystem components (e.g., coastal habitat), and areas designated for spatial planning (e.g., Ecologically and Biologically Significant Areas) for each user-defined area. 

The output from the search includes the following sections: 
1) Information from the National Aquatic Species At Risk Program,
2) Fish and Invertebrates,
3) Cetaceans,
4) Habitat,
5) Areas designated for spatial planning.

#### **How to use this report?**  

-	This document must be circulated to all staff identified as contacts (provided in the report) for each data source to ensure the veracity of inference drawn from the report, and to provide any supplemental information that may support the provision of science advice. Users can also request additional data and/or metadata directly from each contact. 
-	This report is intended for internal DFO use only. Privacy screening (i.e., the rule of 5) is not yet integrated into all data products and summaries generated by the report.
-	The absence of a species in this report should be interpreted as an absence of observation or reporting of the species in the focal area, not necessarily as a true absence of the species. 
-	The focus of this report is on available observations of species presence and not on absences, quantities (e.g., species abundance or biomass), frequency, or catch information. 
-	Because coastal areas of the Scotian Shelf bioregion are generally not adequately sampled to characterize fine-scale ecological characteristics (i.e., species, habitat composition and variability within a sub-regional focal area), the distribution of (some) species featured within the report, when the focal area is near to the coast, should be used as a first-order estimate limited by the spatial-temporal resolution of available data.

This report incorporates information from a variety of sources with differing levels of quality control. Consequently, data sources in the report are categorized into tiers of data quality, and associated usage recommendations.

<br><br>
```{r table tiers read, echo=FALSE, cache=FALSE, include = FALSE}
table_tier <- read.csv("../data/misc/table_tiers_EN.csv")
```
```{r}
knitr::kable(table_tier,align="l", 
      caption = "Quality Tiers defined to describe sources of information queried and summarized in this report.", booktabs = T, escape = F, linesep="") %>%
    kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
```

# **SEARCH RESULTS**  

#### **EMPHASIS ON SPECIES LISTED BY THE <i>SPECIES AT RISK ACT</i>, ASSESSED BY THE COMMITTEE ON THE STATUS OF THE ENDANGERED WILDLIFE IN CANADA (COSEWIC) AND/OR WILD SPECIES**  

The following are definitions relevant for species listed by the _Species At Risk Act_ (SARA), assessed by the Committee on the Status of Endangered Wildlife in Canada (COSEWIC), or included in the Wild Species listings:

- **SARA** - The following text was obtained from the SARA website (URL below). The Species At Risk Act (SARA) was proclaimed in June 2003; it is one part of a three part Government of Canada strategy for the protection of wildlife Species At Risk. This three part strategy also includes commitments under the Accord for the Protection of Species At Risk and activities under the Habitat Stewardship Program for Species At Risk. The purposes of SARA are to prevent Canadian indigenous species, subspecies, and distinct populations from becoming extirpated or extinct, to provide for the recovery of endangered or threatened species, and encourage the management of other species to prevent them from becoming at risk. It applies to all federal lands in Canada; all wildlife species listed as being at risk; and their critical habitat. For more information on SARA visit <https://www.canada.ca/en/environment-climate-change/services/species-risk-public-registry.html> 

- **COSEWIC** - The following text was obtained from the COSEWIC website (URL below): The Committee on the Status of Endangered Wildlife in Canada (COSEWIC) is an independent advisory panel to the Minister of Environment and Climate Change Canada that meets twice a year to assess the status of wildlife Species At Risk of extinction. Members are wildlife biology experts from academia, government, non-governmental organizations and the private sector responsible for designating wildlife species in danger of disappearing from Canada. COSEWIC determines the national status of wild Canadian species, subspecies, varieties or other designatable units that are suspected of being at risk of extinction or extirpation. COSEWIC uses a process based on science and Aboriginal or community knowledge to assess wildlife Species At Risk. All native mammals, birds, reptiles, amphibians, fish, arthropods, molluscs, vascular plants, mosses and lichens are included in COSEWIC's current mandate. For more information on COSEWIC visit <https://www.cosewic.ca/index.php/en-ca/>

- **Wild species** - Every five years, the National General Status Working Group (NGSWG), which includes representatives from federal, provincial and territorial governments, publishes a general report on the status of wildlife species in Canada. These reports are meant to inform Canadians about the status of species in the country, to help prevent species in Canada from becoming extinct as a consequence of human activity, and to identify species that should be considered for evaluation by COSEWIC. For more information about Wild Species reports visit <https://www.wildspecies.ca/home>

{{add_main_sections}}

<!-- HABITAT -->

{{add_appendix}}

<!-- EBSA -->

{{add_ebsa_section}}

<!-- GENERIC END -->

# **CONTRIBUTORS**
```{r read contributors, echo=FALSE, cache=FALSE, include = FALSE}
people <- read.csv("../data/misc/contributors.csv")
people <- people$list
sort(people)
```
List of contributors (listed in alphabetical order): `r knitr::combine_words(people)`. 

For more information about this report, please contact Tana.Worcester@dfo-mpo.gc.ca

# **REFERENCES**    





