# **Search Results for Species at Risk**  

## **Ecologically and Biologically Significant Areas (EBSA)**  
Contact: <https://open.canada.ca/data/en/dataset/d2d6057f-d7c4-45d9-9fd9-0a58370577e0>  
Tier of confidence: **High**  
Search year:  

Ecologically and Biologically Significant Areas (EBSAs) are areas within Canada's oceans that have been identified through formal scientific assessments as having special biological or ecological significance when compared with the surrounding marine ecosystem.  

Failure to define an area as an EBSA does not mean that it is unimportant ecologically. All areas serve ecological functions to some extent and require sustainable management. Rather, areas identified as EBSAs should be viewed as the most important areas where, with existing knowledge, regulators and marine users should be particularly risk averse to ensure ecosystems remain healthy and productive.

#### **EBSA search results**

<!-- ```{r read other species database files for other species, echo=FALSE, include=FALSE, cache=FALSE}
EBSA <- st_read("../../../Data/Zones/DFO_EBSA/DFO_EBSA.shp", quiet=TRUE)
EBSA_shp <- st_transform(EBSA, crs = 4326)
```

```{r echo=FALSE, results='asis'}
#function for overlap
EBSA_overlap(EBSA_shp=EBSA_shp, PEZ_poly_st= PEZ_poly_st)
```

```{r echo=FALSE, results='asis'}
#function for report
EBSA_report(EBSA_shp=EBSA_shp, PEZ_poly_st= PEZ_poly_st)
```

```{r echo=FALSE, results='asis'}
#function for report url
EBSA_reporturl(EBSA_shp=EBSA_shp, PEZ_poly_st= PEZ_poly_st)
```

```{r echo=FALSE, results='asis'}
#function for location
EBSA_location(EBSA_shp=EBSA_shp, PEZ_poly_st= PEZ_poly_st)
```

```{r echo=FALSE, results='asis'}
#function for bioregion
EBSA_bioregion(EBSA_shp=EBSA_shp, PEZ_poly_st= PEZ_poly_st)
```

```{r Fig X PEZ polygon with all maritime EBSA polygons, fig.height=8, fig.width=11}
plot_EBSA(EBSA_shp, PEZ_poly_st, land_sf)
```
**Fig. 12:** Map showing Ecologically and Biologically Significant Areas (EBSA; pink) relative to the defined Potential Exposure Zone (PEZ; blue) and proposed project polygon (yellow). -->
