## **AREAS DESIGNATED FOR SPATIAL PLANNING**

### **Ecologically and Biologically Significant Areas (EBSA)**

Contact: [carissa.philippe\@dfo-mpo.gc.ca](mailto:carissa.philippe@dfo-mpo.gc.ca){.email}\
Last retrieved on: January 21, 2021 from Open Data\
<https://open.canada.ca/data/en/dataset/d2d6057f-d7c4-45d9-9fd9-0a58370577e0>\
Quality Tier: High\
Security level: none\
Data use constraints: none

Dataset description from the Open Data record [@OpenData_ebsa]: Ecologically and Biologically Significant Areas (EBSAs) are areas within Canada's oceans that have been identified through formal scientific assessments as having special biological or ecological significance when compared with the surrounding marine ecosystem. Failure to define an area as an EBSA does not mean that it is unimportant ecologically. All areas serve ecological functions to some extent and require sustainable management. Rather, areas identified as EBSAs should be viewed as the most important areas where, with existing knowledge, regulators and marine users should be particularly risk averse to ensure ecosystems remain healthy and productive. EBSA information is used to inform marine planning, including environmental assessment and the siting of marine-based activities, by:

-   Informing and guiding project-specific or regional environmental assessments
-   Informing and guiding industries and regulators in their planning and operations, for example: EBSAs have been acknowledged and referred to (often as "Special Areas" or "Potentially Sensitive Areas") in oil and gas related assessments
-   EBSA information has been provided to proponents of submarine cable projects to be used for route planning purposes
-   Informing and guiding Integrated Oceans Management (IOM) process within five Large Ocean Management Areas (LOMAs) and twelve marine bioregions
-   Serving as a basis for the identification of Areas of Interest (AOIs) and of Marine Protected Areas (MPAs) (individually and in the context of planning bioregional networks of MPAs).

#### ***Area-specific EBSA search results***


```{r EBSA-results, echo=FALSE, results='asis'}
#function for overlap
EBSAoutput <- master_intersect(EBSA_sf, mapDataList, getRegion=TRUE)

#function for overlap
Query_output_EBSA <- if(is.null(EBSAoutput$studyData)){
    "* The search area does not overlap with identified Ecologically and Biologically Significant Areas (EBSA)."
  } else {
    "* The search area overlaps with identified Ecologically and Biologically Significant Areas (EBSA)."
  }
writeLines(Query_output_EBSA)

```

```{r EBSA-report, echo=FALSE, results='asis'}
#function for report
EBSA_report(EBSAoutput$studyData, lang="EN")
```


```{r EBSA-region-plot, fig.height=8, fig.width=11, fig.cap= 'Quality Tier: High. Security level: none. Map showing Ecologically and Biologically Significant Areas (EBSA) relative to the search area defined by the user (red outline).'}
if (!is.null(EBSAoutput$regionData)){
  plot_rr_sf(regionMap, EBSAoutput$regionData, "NONE")
}
```

```{r EBSA-area-plot, fig.height=8, fig.width=11, fig.cap= 'Quality Tier: High. Security level: none. Map showing Ecologically and Biologically Significant Areas (EBSA) in the search area defined by the user (red outline).'}
if(!is.null(EBSAoutput$studyData)){
  plot_rr_sf(areaMap, EBSAoutput$mapData, "NONE")
}
```

### **`r mpa_rr$title`** {#MPA-section}


```{r MPA-section, results='asis'}
write_meta(mpa_rr)
writeLines(noquote(mpa_rr$text))

```

#### ***Area-specific Draft Conservation Network Design search results ***

```{r MPA-load-data, results='asis'}
mpaCols <- c("darkorchid", "lawngreen", "dodgerblue2", "cyan3")
mpaAlphas <- c(0.5, 0.5, 0.5, 0.5)
names(mpaCols) <- levels(as.factor(mpa_rr$data_sf[[mpa_rr$attribute]]))
names(mpaAlphas) <- levels(as.factor(mpa_rr$data_sf[[mpa_rr$attribute]]))

mpaClipped <- master_intersect(mpa_rr$data_sf,  mapDataList, getRegion=TRUE)

if(!is.null(mpaClipped$studyData)) {
  mpaTable <- mpa_table(mpaClipped$studyData)
} else {
  mpaTable <- NULL
}

#function for overlap
mpaCheckOuput <- if(!is.null(mpaClipped$studyData)){
    "* There are relevant records of areas that are part of the Draft Conservation Network Design in the search area."
  } else {
    "* There are no relevant records of areas that are part of the Draft Conservation Network Design in the search area."
  }

writeLines(mpaCheckOuput)
```

```{r mpa-region-plot, fig.height=8, fig.width=11, fig.cap= 'Quality Tier: High. Security level: none.Map of the Draft Conservation Network Design for the Scotian Shelf-Bay of Fundy Bioregion. '}
if (!is.null(mpaClipped$regionData)){
  mpaLabels <- filter(st_centroid(mpaClipped$regionData), Id > 0) %>% dplyr::select(c("Id"))
  plot_rr_sf(regionMap, mpaClipped$regionData, mpa_rr$attribute, colorMap = mpaCols,
                            labelData = mpaLabels, labelAttribute = "Id", alphaMap = mpaAlphas)
}
```

```{r mpa-area-plot, fig.height=8, fig.width=11, fig.cap= 'Quality Tier: High. Security level: none. Map of the Draft Conservation Network Design in the search area defined by the user (red outline).'}
if(!is.null(mpaClipped$studyData)){
  mpaStudyLabels <- filter(st_centroid(mpaClipped$mapData), Id > 0) %>% dplyr::select(c("Id"))

  plot_rr_sf(areaMap, mpaClipped$mapData, mpa_rr$attribute, colorMap = mpaCols,
             labelData = mpaStudyLabels, labelAttribute = "Id", alphaMap = mpaAlphas)
}
```

```{r mpa-table, echo=FALSE, results='asis', caption="MPA table"}
if (!is.null(mpaTable)) {
  knitr::kable(mpaTable, align="l", caption="Quality Tier: High Security level: none. Area and names of Marine Protected Areas located within study area..</b>", booktabs = T, escape = F, linesep="") %>% kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}
```
