``` {r load-planning-data, echo=FALSE}
filesLoaded <- load_rdata(c("ebsa_rr", "conservationSites_rr"), "MAR", env = environment())

```


## **AREAS DESIGNATED FOR SPATIAL PLANNING**

This section describes information relevant to spatial planning from a variety of sources. Area-specific outputs are provided in sub-sections labeled according to the data source. Descriptions of the source data and appropriate references and contacts are provided at the beginning of each sub-section.

<!-- ### **Ecologically and Biologically Significant Areas (EBSA)** -->

### **`r ebsa_rr$title$en` **

```{r EBSA-meta, results='asis'}
write_meta(ebsa_rr, "EN")
```
EBSA Story Map: <https://gisp.dfo-mpo.gc.ca/portal/apps/MapJournal/index.html?appid=b91f85de60f44a7b90633e4b43e3916a>

Dataset description from the Open Data record (DFO 2016a):
```{r EBSA-text, results='asis'}
writeLines(noquote(ebsa_rr$text$en))

```

#### ***Area-specific EBSA search results***

```{r EBSA-results, echo=FALSE, results='asis'}
#function for overlap
EBSAoutput <- master_intersect(ebsa_rr$data_sf, mapDataList, getRegion=TRUE)

#function for overlap
Query_output_EBSA <- if(is.null(EBSAoutput$studyData)){
    "* The search area does not overlap with identified Ecologically and Biologically Significant Areas (EBSA)."
  } else {
    "* The search area overlaps with identified Ecologically and Biologically Significant Areas (EBSA)."
  }
writeLines(Query_output_EBSA)

```


```{r EBSA-table,  echo=FALSE, results='asis'}
EBSATable <- EBSA_report(EBSAoutput$studyData, lang="EN")
if (!is.null(EBSATable)){
   knitr::kable(EBSATable, align="l", caption="Details for EBSA's overlapping the study area.</b>", booktabs = T, escape = F, linesep="") %>% kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}
```

```{r EBSA-region-plot, fig.height=8, fig.width=11, fig.cap= 'Quality Tier: High. Security level: none. Map showing Ecologically and Biologically Significant Areas (EBSA) relative to the search area defined by the user (red outline).'}
if (!is.null(EBSAoutput$regionData)){
  plot_rr_sf(regionMap, EBSAoutput$regionData, ebsa_rr$attribute)
}
```

```{r EBSA-area-plot, fig.height=8, fig.width=11, fig.cap= 'Quality Tier: High. Security level: none. Map showing Ecologically and Biologically Significant Areas (EBSA) in the search area defined by the user (red outline).'}
if(!is.null(EBSAoutput$studyData)){
  plot_rr_sf(areaMap, EBSAoutput$mapData, ebsa_rr$attribute)
}
```

### **Draft Conservation Network Design** {#MPA-section}

```{r MPA-section, results='asis'}
write_meta(conservationSites_rr, "EN")

```

A key milestone and focal point for the planning process is the Draft Conservation Network Design, which is a map of both existing and potential future marine protected areas (MPAs) and other spatial conservation areas that would contribute to the long-term conservation of marine biodiversity in the bioregion. The Draft Design was originally drafted in 2017 following an extensive spatial conservation analysis led by Fisheries and Oceans Canada (DFO). While some discussion on the Draft Design has been ongoing with provincial and First Nations partners since that time, events such as the COVID-19 pandemic have limited the scope and pace of the overall engagement process.

Marine Planning and Conservation at DFO has initiated a two-phased engagement process on the Draft Design to inform the completion of a Conservation Network Plan for the Scotian Shelf-Bay of Fundy bioregion. During Phase 1, DFO will be undertaking targeted discussions with federal and provincial departments, First Nations and Indigenous groups, and key stakeholders, such as the fishing industry. The primary purpose of Phase 1 is to provide those with previous involvement in the process with an opportunity to review and provide written feedback on the Draft Design by December 31, 2021. In 2022, the Draft Design will be revised based on the feedback received. Phase 2 is planned for early 2023 and will include a broader public engagement process. The Marine Conservation Network Plan will be completed by 2024 and will be updated periodically as new information becomes available.

It is important to note that Marine Conservation Network Plan will be aligned with a future Marine Spatial Plan for the Scotian Shelf-Bay of Fundy bioregion. The overall intent is to ensure an effective balance among ecological, socio-economic and cultural objectives in the use, management and conservation of our marine environment and spaces. DFO and its partners will be providing further information on the bioregional Marine Spatial Planning (MSP) process in the near future.

#### ***Area-specific Draft Conservation Network Design search results ***

```{r MPA-load-data, results='asis'}
mpaCols <- c("dodgerblue3", "red", "darkorchid", "lawngreen",  "cyan3")
mpaAlphas <- c(0.5, 0.5, 0.5, 0.5, 0.5)
names(mpaCols) <- levels(as.factor(conservationSites_rr$data_sf[[conservationSites_rr$attribute]]))
names(mpaAlphas) <- levels(as.factor(conservationSites_rr$data_sf[[conservationSites_rr$attribute]]))

mpaClipped <- master_intersect(conservationSites_rr$data_sf,  mapDataList, getRegion=TRUE)

if(!is.null(mpaClipped$studyData)) {
  mpaTable <- mpa_table(mpaClipped$studyData)
} else {
  mpaTable <- NULL
}

#function for overlap
mpaCheckOuput <- if(!is.null(mpaClipped$studyData)){
    "* There are relevant records of areas that are part of the Draft Conservation Network Design in the search area."
  } else {
    "* There are no relevant records of areas that are part of the Draft Conservation Network Design in the search area."
  }

writeLines(mpaCheckOuput)
```

```{r mpa-region-plot, fig.height=8, fig.width=11, fig.cap= 'Quality Tier: High. Security level: none.Map of the Draft Conservation Network Design for the Scotian Shelf-Bay of Fundy Bioregion. Boundaries of the proposed new sites are preliminary and subject to change following engagement and consultation. '}
if (!is.null(mpaClipped$regionData)){
  plot_rr_sf(regionMap, mpaClipped$regionData, conservationSites_rr$attribute, outlines=FALSE, colorMap = mpaCols,
                            alphaMap = mpaAlphas)
}
```

```{r mpa-area-plot, fig.height=8, fig.width=11, fig.cap= 'Quality Tier: High. Security level: none. Map of the Draft Conservation Network Design in the search area defined by the user (red outline). Please see table below for names of each specific area. Boundaries of the proposed new sites are preliminary and subject to change following engagement and consultation.'}
if(!is.null(mpaClipped$studyData)){
  mpaStudyLabels <- filter(st_centroid(mpaClipped$mapData), Id > 0) %>% dplyr::select(c("Id"))

  plot_rr_sf(areaMap, mpaClipped$mapData, conservationSites_rr$attribute, colorMap = mpaCols,
             labelData = mpaStudyLabels, labelAttribute = "Id", alphaMap = mpaAlphas)
}
```

```{r mpa-table, echo=FALSE, results='asis', caption="MPA table"}
if (!is.null(mpaTable)) {
  knitr::kable(mpaTable, align="l", caption="Quality Tier: High Security level: none. Area and names of spatial conservation areas that overlap the search area..</b>", booktabs = T, escape = F, linesep="") %>% kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}
```
