
---
output:
  bookdown::html_document2:
    number_sections: FALSE
    theme: paper
bibliography: '`r here::here("app/data/mybiblio.bib")`'
---
```{r child = here::here("sections/commonSections/commonIntro.Rmd")}
if (FALSE) { #load in data:
  lapply(list.files(here::here("app/R"), pattern = ".[Rr]$", full.names = TRUE), source)
  studyArea <- sf::st_read(here::here("app/output/geoms_slc.geojson")) 
  intro_setup(studyArea, env = environment())  
}
```

#### ***Critical Habitat of Species at Risk*** {#crithab-section}   

```{r crithab-load, include=FALSE}
load_rdata(c("crithab_rr", "leatherback_rr"), "MAR", env = environment())
```

```{r crtihab-meta, results='asis'}
write_meta(crithab_rr, "EN")
```
Data use constraints for Leatherback Sea Turtle draft critical habitat: DFO INTERNAL USE ONLY

Dataset description from the Open Data record [@OpenData_SARcriticalhabitat]:
```{r crithab-text, results='asis'}
writeLines(noquote(crithab_rr$text$en))
```

Critical habitat presented in this section are available in the Government of Canada Open Data portal, with the exception of draft critical habitat for Leatherback Sea Turtle, for which delineation of critical habitat is currently under review. Draft critical habitat for Leatherback Sea Turtle is available in the internal Species at Risk GIS tool and will be available in Open Data once it has been included in a proposed or final Recovery Strategy.


#### ***Area-specific critical habitat search results***

```{r crithab-results, echo=FALSE, results='asis'}
# plotted with colour
legendNameCrithab <- "Common Name"
outputListCrithab <- master_intersect(crithab_rr$data_sf, mapDataList)

# plotted in single colour
outputListLB <- master_intersect(leatherback_rr$data_sf, mapDataList)

critHabCheck <- !is.null(outputListCrithab$studyData) | !is.null(outputListLB$studyData)

```

```{r crithab-table-gen, echo=FALSE, results='asis'}
if (critHabCheck) {
  critTable <- table_crit(outputListCrithab$studyData, outputListLB$studyData, "EN")  
  summaryHabTable <- add_to_hab_summary(summaryHabTable, "CH", "[SAR Critical Habitat](#crithab-section)", critTable, "Common Name", "Common Name")
}
```

```{r crithab-check, comment="", prompt=TRUE, echo=FALSE, results='asis'}
 Query_output_crit <- if(critHabCheck){
   "* The search area overlaps with defined Species at Risk Critical Habitat."
 } else {
   "* The search area does not overlap with defined Species at Risk Critical Habitat."
 }
 writeLines(Query_output_crit)
```
<br>

```{r crithab-table, echo=FALSE, results='asis'}
if(critHabCheck){
  knitr::kable(critTable, caption=paste(write_caption_blurb(crithab_rr, "EN"), "Species at Risk listed as Endangered or Threatened under the <i>Species at Risk Act</i> (SARA) with their critical habitat located within the search area. Critical habitat is defined under section 2 of SARA as: “the habitat that is necessary for the survival or recovery of a listed wildlife species and that is identified as the species’ critical habitat in the recovery strategy or in an action plan for the species”. Critical habitat is identified in a species’ Recovery Strategy or Action Plan, posted on the [SAR Public Registry](http://www.sararegistry.gc.ca). This is <b>not</b> the authoritative source or advice for Species at Risk data. Please access the Species at Risk [GIS tool](http://dfonl7swvgip001.ent.dfo-mpo.ca/Html5Viewer/index.html?viewer=NationalSARMap_EN&LayerTheme=0&locale=en-US) to create an authoritative SARA report."), booktabs = T, escape = F, linesep="") %>% kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
}

```
<br>
```{r crithab-region-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(crithab_rr, "EN"), 'Map summarizing critical habitat of Species at Risk listed as Endangered or Threatened under the <i>Species at Risk Act</i> (SARA) in the Scotian Shelf Bioregion. Please see table above for complementary information. Critical habitat is defined under section 2 of SARA as: “the habitat that is necessary for the survival or recovery of a listed wildlife species and that is identified as the species’ critical habitat in the recovery strategy or in an action plan for the species.” Critical habitat is identified in a species’ Recovery Strategy or Action Plan, posted on the [SAR Public Registry](http://www.sararegistry.gc.ca). This is not the authoritative source or advice for Species at Risk data. Please access the Species at Risk [GIS tool](http://dfonl7swvgip001.ent.dfo-mpo.ca/Html5Viewer/index.html?viewer=NationalSARMap_EN&LayerTheme=0&locale=en-US) to create an authoritative report.')}
if (!is.null(crithab_rr$data_sf)){
  critPlotList <- plot_rr_sf(regionMap, crithab_rr$data_sf,
                             crithab_rr$attribute, legendName = legendNameCrithab,
                             outlines=FALSE, getColorMap=TRUE)
  critPlotList$polyMap
}  
```
<br>
```{r crithab-area-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(crithab_rr, "EN"), 'Map summarizing critical habitat of Species at Risk, listed as Endangered or Threatened under the <i>Species at Risk Act</i> (SARA), located within the search area (red outline)')}
if (!is.null(outputListCrithab$mapData)){
  plot_rr_sf(areaMap, outputListCrithab$mapData, crithab_rr$attribute,
             legendName = legendNameCrithab, outlines=FALSE, colorMap = critPlotList$colorMap)
}  
```
<br>
```{r leatherback-region-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(leatherback_rr, "EN"), 'Map summarizing draft critical habitat of Leatherback Sea Turtle, relative to the search area. Draft critical habitat for the species is based on information DFO published as an update to Science advice regarding important habitat for the Leatherback Sea Turtle: https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2020/2020_041-eng.html')}
if (!is.null(leatherback_rr$data_sf)){
  plot_rr_sf(regionMap, leatherback_rr$data_sf, leatherback_rr$attribute)
}   
```
<br>
```{r leatherback-area-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(leatherback_rr, "EN"), 'Map summarizing the draft critical habitat of Leatherback Sea Turtle located within the search area (red outline).')}
if (!is.null(outputListLB$mapData)){
  plot_rr_sf(areaMap, outputListLB$mapData, leatherback_rr$attribute)
}
```
