
---
output:
  bookdown::html_document2:
    number_sections: FALSE
    theme: paper
bibliography: '`r here::here("app/data/mybiblio.bib")`'
---
```{r crithab-load-common, child = here::here("reports/sections/commonSections/commonIntro.Rmd")}
```

```{r eval=FALSE}
if (FALSE) { #load in data:
  lapply(list.files(here::here("reports/R"), pattern = ".[Rr]$", full.names = TRUE), source)
  studyArea <- sf::st_read(here::here("app/output/geoms_slc.geojson")) 
  intro_setup(studyArea, env = environment())  
}
```

### **Critical Habitat of Species at Risk** {#crithab-section}   

```{r crithab-load, include=FALSE}
load_rdata(c("crithab_rr", "draftCritHab_rr"), regionStr, env = environment())
```

```{r crtihab-meta, results='asis'}
write_meta(draftCritHab_rr, "EN")
```

Dataset description from the Open Data record [@OpenData_SARcriticalhabitat]:
```{r crithab-text, results='asis'}
writeLines(noquote(crithab_rr$text$en))
```

Critical habitat presented in this section are available in the Government of Canada Open Data portal, with the exception of draft critical habitat, for which delineation of critical habitat is currently under review. Draft critical habitat is available in the internal Species at Risk GIS tool and will be available in Open Data once it has been included in a proposed or final Recovery Strategy.


##### *Area-Specific Critical Habitat Search Results*

```{r crithab-results, echo=FALSE, results='asis'}
# plotted with colour
legendNameCrithab <- "Common Name"
outputListCrithab <- master_intersect(crithab_rr$data_sf, mapDataList)
critHabCheck <- !is.null(outputListCrithab$studyData)

summaryIntroTable <- add_row_to_intro_summary(summaryIntroTable, name="[Critical Habitat](#crithab-section)", result=critHabCheck)


outputListDraft <- master_intersect(draftCritHab_rr$data_sf, mapDataList)
draftCheck <- !is.null(outputListDraft$studyData)

```

```{r crithab-table-gen, echo=FALSE, results='asis'}
if (critHabCheck) {
  critTable <- table_crit(outputListCrithab$studyData, "EN")  
  summaryHabTable <- add_to_hab_summary(summaryHabTable, "CH", "[SAR Critical Habitat](#crithab-section)", critTable, "Common Name", "Common Name")
}
```

```{r draft-crithab-table-gen, echo=FALSE, results='asis'}
if (draftCheck) {
  draftTable <- table_crit(outputListDraft$studyData, "EN")  
  summaryHabTable <- add_to_hab_summary(summaryHabTable, "CH", "[SAR Draft Critical Habitat](#crithab-section)", draftTable, "Common Name", "Common Name")
}
```

```{r crithab-check, comment="", prompt=TRUE, echo=FALSE, results='asis'}
 Query_output_crit <- if(critHabCheck){
   "* The search area overlaps with defined Species at Risk critical habitat."
 } else {
   "* The search area does not overlap with defined Species at Risk critical habitat."
 }
 writeLines(Query_output_crit)
```
<br>

```{r crithab-table, echo=FALSE, results='asis'}
if(critHabCheck){
  knitr::kable(critTable, caption=paste(write_caption_blurb(crithab_rr, "EN"), "Species at Risk listed as Endangered or Threatened under the Species at Risk Act [@SARA2002] with their critical habitat located within the search area. Critical habitat is defined under section 2 of SARA as, “the habitat that is necessary for the survival or recovery of a listed wildlife species and that is identified as the species’ critical habitat in the Recovery Strategy or in an Action Plan for the species”. Critical habitat is identified in a species’ Recovery Strategy or Action Plan, posted on the [SAR Public Registry](http://www.sararegistry.gc.ca). This is <b>not</b> the authoritative source or advice for Species at Risk data. Please access the Species at Risk [GIS tool](http://dfonl7swvgip001.ent.dfo-mpo.ca/Html5Viewer/index.html?viewer=NationalSARMap_EN&LayerTheme=0&locale=en-US) to create an authoritative SARA report."), booktabs = T, escape = F, linesep="") %>% kableExtra::kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
}

```
<br>
```{r crithab-region-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(crithab_rr, "EN"), 'Critical habitat of Species at Risk listed as Endangered or Threatened under the Species at Risk Act [@SARA2002] in the Scotian Shelf Bioregion. Please see table above for complementary information. Critical habitat is defined under section 2 of SARA as, “the habitat that is necessary for the survival or recovery of a listed wildlife species and that is identified as the species’ critical habitat in the Recovery Strategy or in an Action Plan for the species.” Critical habitat is identified in a species’ Recovery Strategy or Action Plan, posted on the [SAR Public Registry](http://www.sararegistry.gc.ca). This is not the authoritative source or advice for Species at Risk data. Please access the Species at Risk [GIS tool](http://dfonl7swvgip001.ent.dfo-mpo.ca/Html5Viewer/index.html?viewer=NationalSARMap_EN&LayerTheme=0&locale=en-US) to create an authoritative report. The search area is shown as a red outline, and a more detailed view is shown in the figure below, if relevant data are present. Dashed grey lines indicate international boundaries. Data were obtained from @OpenData_SARcriticalhabitat.')}
if (!is.null(crithab_rr$data_sf)){
  critPlotList <- plot_rr_sf(regionMap, crithab_rr$data_sf,
                             crithab_rr$attribute, legendName = legendNameCrithab,
                             outlines=FALSE, getColorMap=TRUE)
  critPlotList$polyMap
}  
```
<br>
```{r crithab-area-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(crithab_rr, "EN"), 'Critical habitat of Species at Risk, listed as Endangered or Threatened under the Species at Risk Act (SARA), located within the search area (red outline). Data were obtained from @OpenData_SARcriticalhabitat.')}
if (!is.null(outputListCrithab$mapData)){
  plot_rr_sf(areaMap, outputListCrithab$mapData, crithab_rr$attribute,
             legendName = legendNameCrithab, outlines=FALSE, colorMap = critPlotList$colorMap)
}  
```

```{r draft-crithab-table, echo=FALSE, results='asis'}
if(draftCheck){
  knitr::kable(draftTable, caption=paste(write_caption_blurb(draftCritHab_rr, "EN"), "Species at Risk listed as Endangered or Threatened under the Species at Risk Act [@SARA2002] with their critical habitat located within the search area. Critical habitat is defined under section 2 of SARA as, “the habitat that is necessary for the survival or recovery of a listed wildlife species and that is identified as the species’ critical habitat in the Recovery Strategy or in an Action Plan for the species”. Critical habitat is identified in a species’ Recovery Strategy or Action Plan, posted on the [SAR Public Registry](http://www.sararegistry.gc.ca). This is <b>not</b> the authoritative source or advice for Species at Risk data. Please access the Species at Risk [GIS tool](http://dfonl7swvgip001.ent.dfo-mpo.ca/Html5Viewer/index.html?viewer=NationalSARMap_EN&LayerTheme=0&locale=en-US) to create an authoritative SARA report."), booktabs = T, escape = F, linesep="") %>% kableExtra::kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
}

```
<br>
```{r draft-crithab-region-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(crithab_rr, "EN"), 'Critical habitat of Species at Risk listed as Endangered or Threatened under the Species at Risk Act [@SARA2002] in the Scotian Shelf Bioregion. Please see table above for complementary information. Critical habitat is defined under section 2 of SARA as, “the habitat that is necessary for the survival or recovery of a listed wildlife species and that is identified as the species’ critical habitat in the Recovery Strategy or in an Action Plan for the species.” Critical habitat is identified in a species’ Recovery Strategy or Action Plan, posted on the [SAR Public Registry](http://www.sararegistry.gc.ca). This is not the authoritative source or advice for Species at Risk data. Please access the Species at Risk [GIS tool](http://dfonl7swvgip001.ent.dfo-mpo.ca/Html5Viewer/index.html?viewer=NationalSARMap_EN&LayerTheme=0&locale=en-US) to create an authoritative report. The search area is shown as a red outline, and a more detailed view is shown in the figure below, if relevant data are present. Dashed grey lines indicate international boundaries. Data were obtained from @OpenData_SARcriticalhabitat.')}
if (!is.null(draftCritHab_rr$data_sf)){
  draftPlotList <- plot_rr_sf(regionMap, draftCritHab_rr$data_sf,
                             draftCritHab_rr$attribute, legendName = legendNameCrithab,
                             outlines=FALSE, getColorMap=TRUE)
  draftPlotList$polyMap
}  
```
<br>
```{r draft-crithab-area-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(crithab_rr, "EN"), 'Critical habitat of Species at Risk, listed as Endangered or Threatened under the Species at Risk Act (SARA), located within the search area (red outline). Data were obtained from @OpenData_SARcriticalhabitat.')}
if (!is.null(outputListDraft$mapData)){
  plot_rr_sf(areaMap, outputListDraft$mapData, draftCritHab_rr$attribute,
             legendName = legendNameCrithab, outlines=FALSE, colorMap = draftPlotList$colorMap)
}  
```

