---
output:
  bookdown::html_document2:
    number_sections: FALSE
    theme: paper
bibliography: '`r here::here("app/data/mybiblio.bib")`'
---

```{r sarsearch-load-common, child = here::here("reports/sections/commonSections/commonIntro.Rmd")}
```

```{r eval=FALSE}
if (FALSE) { 
  # load in generic data, e.g.functions, study area, and base maps into the 
  # environment, when knitting, these will be loaded through the child rmd.
  lapply(list.files(here::here("reports/R"), pattern = ".[Rr]$", full.names = TRUE), source)
  studyArea <- sf::st_read(here::here("app/output/geoms_slc.geojson"))
  intro_setup(studyArea, env = environment())
}
```

### **Sarsearch DMapps Data** {#sarsearch-section}

```{r sarsearch-load, include=FALSE}
# load in section specific data
load_rdata(c("sarsearch_rr"), regionStr, env = environment())

```

```{r sarsearch-meta, results='asis'}
# metadata blurb at start of each section
write_meta(sarsearch_rr, "EN")
```

Species data collected in the Species At Risk (SAR) search application (part of DFO's DMapps suite) was extracted and is presented below.
-	The data originates from both external and internal sources, and must not to be shared or used outside DFO. 
- Sources include data mining from COSEWIC reports.
-	The data is not comprehensive in any way. It is likely that there are records of occurrence for any given species that have not been included or represented and likely does not represent the latest records, findings, or distribution for any given species. 
-	Although the data is accurate based on its original source, it is from a variety of sources and varies in quality depending on the source for any given record.
-	While every reasonable effort has been made to ensure that the data is correct, DFO Species at Risk Program does not warrant or guarantee the accuracy, completeness, or currency of the data for any specific use. 
-	Data that are represented only by “Regions” in the record and/or the map only implies that the species has been found in the specified region(s). “Regions” must not be used as polygons of distribution.
-	A data point can either represent the exact location at which a species was found or may be used to indicate the presence of a species in any given waterbody. Please consult all information for any given record before making any interpretation. 


#### *Area-specific Sarsearch results*
```{r sarsearch-results, include=FALSE, cache=FALSE}
# clip the data to the Study and Map areas:
outputList <- master_intersect(sarsearch_rr$data_sf, mapDataList, getRegion = TRUE)


# summary intro table
introResult <- !is.null(outputList$studyData)
summaryIntroTable <- add_row_to_intro_summary(summaryIntroTable, name="[Sarsearch DMapp](#sarsearch-section)", result=introResult)


sarsearchTable <- sf::st_drop_geometry(outputList$studyData)
sarsearchTable <- dplyr::select(sarsearchTable, c(species_name, year, name, source, notes))
names(sarsearchTable) <- c("Species Name", "Year", "Location Name", "Source", "Notes")
sarsearchTable[is.na(sarsearchTable)] <- ""
row.names(sarsearchTable) <- NULL

```

```{r sarsearch-check, echo=FALSE, results='asis',}
# Check if there is any data in the study area
sarsearchReport <- if (is.null(outputList$studyData)) {
  "* There are no relevant SAR search records for this search area."
} else {
  "* There are relevant SAR search records for this search area."
}
writeLines(noquote(sarsearchReport))
```

```{r sarsearch-region-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(sarsearch_rr, "EN"), 'Map showing the search area defined by the user (red outline) used to query information from Sarsearch records.')}
if (!is.null(outputList$regionData)) {
  pointData <- outputList$regionData[sf::st_is(outputList$regionData$geometry, c("POINT", "MULTIPOINT")), ]
  lineData <- outputList$regionData[sf::st_is(outputList$regionData$geometry, "LINESTRING"), ]
  polyData <- outputList$regionData[sf::st_is(outputList$regionData$geometry, "POLYGON"), ]
  
  polyMap <- plot_rr_sf(regionMap, polyData, attribute = sarsearch_rr$attribute, alpha = 0.5)
  lineMap <- plot_rr_sf(polyMap, lineData)
  plot_rr_sf(lineMap, pointData, attribute = sarsearch_rr$attribute)
}
```

```{r sarsearch-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(sarsearch_rr, "EN"), 'Map showing the search area defined by the user (red outline) used to query information from Sarsearch records.')}
if (!is.null(outputList$studyData)) {
  pointData <- outputList$mapData[sf::st_is(outputList$mapData$geometry, c("POINT", "MULTIPOINT")), ]
  lineData <- outputList$mapData[sf::st_is(outputList$mapData$geometry, "LINESTRING"), ]
  polyData <- outputList$mapData[sf::st_is(outputList$mapData$geometry, "POLYGON"), ]
  
  polyMap <- plot_rr_sf(areaMap, polyData, attribute = 
               sarsearch_rr$attribute, alpha = 0.5)
  lineMap <- plot_rr_sf(polyMap, lineData)
  plot_rr_sf(lineMap, pointData, attribute = 
               sarsearch_rr$attribute)
}
```
<br>
```{r sarsearch-table}
if (!is.null(outputList$studyData)) {
  if (nrow(sarsearchTable) > 0) {
    knitr::kable(sarsearchTable, align = "l", caption = paste("\\label{tab:sarsearch_table}", write_caption_blurb(sarsearch_rr, "EN"), "SAR search records of species contained within the search area and listed by the Species At Risk Act (SARA), and/or assessed by the Committee on the Status of Endangered Wildlife in Canada (COSEWIC). Frequency represents the subset of the sampling locations out of the total where each species is present. <b>The absence of a species in this table should be interpreted as an absence of reporting, not necessarily as an absence of the species in the area. </b>"), booktabs = T, escape = F, linesep = "") %>% kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
  }
}
```
