# **SEARCH RESULTS: SPECIES FOCUS**

This module describes outputs of species derived from a variety of data sources, internal and external to DFO. Species that have been listed under the Species at Risk Act (SARA), or assessed by the Committee on the Status of Endangered Wildlife in Canada (COSEWIC), are summarized in independent tables. Area-specific outputs are provided in sub-sections labelled according to each data source. Data descriptions, references and contact information are provided at the beginning of each sub-section. The following are definitions relevant for species listed by the Species at Risk Act (SARA) or assessed by the Committee on the Status of Endangered Wildlife in Canada (COSEWIC).

- SARA - The following text was obtained from the SARA website (URL below). The Species at Risk Act (SARA) was proclaimed in June 2003; it is one part of a three-part Government of Canada strategy for the protection of wildlife Species At Risk. This three-part strategy also includes commitments under the Accord for the Protection of Species At Risk and activities under the Habitat Stewardship Program for Species At Risk. The purposes of SARA are to prevent Canadian indigenous species, subspecies, and distinct populations from becoming extirpated or extinct, to provide for the recovery of endangered or threatened species, and encourage the management of other species to prevent them from becoming at risk. It applies to all federal lands in Canada; all wildlife species listed as being at risk; and their critical habitat. For more information on SARA visit https://www.canada.ca/en/environment-climate-change/services/species-risk-public-registry.html

- COSEWIC - The following text was obtained from the COSEWIC website (URL below): The Committee on the Status of Endangered Wildlife in Canada (COSEWIC) is an independent advisory panel to the Minister of Environment and Climate Change Canada that meets twice a year to assess the status of wildlife Species At Risk of extinction. Members are wildlife biology experts from academia, government, non-governmental organizations and the private sector responsible for designating wildlife species in danger of disappearing from Canada. COSEWIC determines the national status of wild Canadian species, subspecies, varieties or other designatable units that are suspected of being at risk of extinction or extirpation. COSEWIC uses a process based on science and Aboriginal or community knowledge to assess wildlife Species At Risk. All native mammals, birds, reptiles, amphibians, fish, arthropods, molluscs, vascular plants, mosses and lichens are included in COSEWIC’s current mandate. For more information on COSEWIC visit https://www.cosewic.ca/index.php/en-ca/

## **SPECIES AT RISK DISTRIBUTION & CRITICAL HABITAT DATA: SARA GEODATABASE**    
**Contact:** Carolyn.Bakelaar@dfo-mpo.gc.ca  
**Internal GIS Tool URL:** <http://dfonl7swvgip001.ent.dfo-mpo.ca/Html5Viewer/index.html?viewer=NationalSARMap_EN&LayerTheme=0&locale=en-US#>  

This section describes Species at Risk distribution/range, and critical habitat maps. The official source of information for Species at Risk is the Species at Risk Public Registry www.sararegistry.gc.ca, and the National Aquatic Species at Risk Geodatabase.

DFO’s Species at Risk Program is responsible for carrying out DFO’s mandate under the _Species at Risk Act_ (SARA), and is an authoritative source of information for aquatic Species at Risk.

DFO’s Species at Risk Program has published Species at Risk distribution/range and critical habitat maps on the Government of Canada Open Data portal, and it has also developed internal and public interactive National Species at Risk Mapping Tools. As described by the National Species at Risk Mapping Tool - Frequently Asked Questions (http://dfonl7swvgip001/NationalSARDemo/LinkDocs/Help/FAQsEN_FR.pdf), the Species at Risk Program in the National Headquarters (NHQ) initiated the tool to facilitate project assessment under the _Fisheries Act_ and SARA. It uses a Geographic Information System (GIS) and interactive display of reproducible, spatially-referenced data for aquatic SARA-listed species. The data contained in the tool are maintained by regional SARA program offices, coordinated by the NHQ Species at Risk Program (Steering Committee). Data are added in concert with the development of SARA recovery documents and SARA listing timelines.

This report is *not* the authoritative advice on Species at Risk data. Please access the Species at Risk GIS tool mentioned above to create an authoritative report, particularly if any of the data sources are at, or near, the search area. Below, we provide a list and examination of data products that may overlap with the user-defined search area.

```{r child = here::here("reports/sections/sardist/sardist_en.Rmd")}
```

```{r child = here::here("reports/sections/crithab/crithab_en.Rmd")}
```

```{r child = here::here("reports/sections/permits/permits_en.Rmd")}
```
