---
output:
  bookdown::html_document2:
    number_sections: FALSE
    theme: paper
bibliography: '`r here::here("app/data/mybiblio.bib")`'
---

```{r offshoreScallop-load-common, child = here::here("reports/sections/commonSections/commonIntro.Rmd")}
```

```{r eval=FALSE}
if (FALSE) { 
  # load in generic data, e.g.functions, study area, and base maps into the 
  # environment, when knitting, these will be loaded through the child rmd.
  lapply(list.files(here::here("reports/R"), pattern = ".[Rr]$", full.names = TRUE), source)
  studyArea <- sf::st_read(here::here("app/output/geoms_slc.geojson"))
  intro_setup(studyArea, env = environment())
}
```

### **Offshore Scallop** {#offshore-scallop-section}

```{r offshoreScallop-load, include=FALSE}
# load in section specific data
load_rdata(c("offshoreScallop_rr"), regionStr, env = environment())

```

```{r offshoreScallop-meta, results='asis'}
# metadata blurb at start of each section
write_meta(offshoreScallop_rr, "EN")
```

The Offshore Scallop Survey Database (SCALOFF) contains data collected through Collaborative Agreements (formerly Joint Project Agreements) between DFO Science and the Seafood Producers Association of Nova Scotia (SPANS). The Offshore Scallop Survey collects data on the stocks of Sea Scallop (*Placopecten magellanicus*) on the Eastern Scotian Shelf and the Canadian side of Georges Bank and both Sea Scallop and Iceland Scallop (*Chlamys islandica*) on Banquereau Bank. These stocks correspond to the DFO management units known as Scallop Fishing Areas (SFA) 25, 26, and 27, and the survey data are the primary source of fishery-independent information used in the scallop stock assessments.


The Offshore Scallop Survey has occurred annually since 1978 with few exceptions, but spatial coverage and survey designs have changed over time. Regardless of survey design, the same sampling protocol is followed: At each survey station, the 8-ft  scallop dredge lined with 48mm mesh is towed for 10 minutes, and all sea scallops(and Icelandic Scallops on Banquereau and St.Pierre Banks) are counted and assigned to 5mm shell height bins (ranging from 0-200mm). Detailed sampling occurs at a selection of the stations, where the exact shell heights and meat weights are recorded for a sub-sample of the scallops caught. The collection of bottom temperature data from the Offshore Scallop surveys began in 2011.  

Under the Collaborative Agreement, survey responsibilities are shared between Project Authorities. At-sea survey activities are directed by the DFO Chief Scientist aboard the survey vessel, which is provided by SPANS. SPANS also provides the necessary crew complement for the survey vessel. DFO Science designs the survey, provides and manages scientific equipment, and validates, archives, and analyzes survey data. A Survey Working Group composed of DFO staff and SPANS members meets prior to each survey to provide input and support.


Data requests are subject to the terms of the Collaborative Agreement. Please contact Freya Keyser (DFO Offshore Scallop Biologist, freya.keyser@dfo-mpo.gc.ca) with details on your request, and you will be guided through the Offshore Scallop Survey data request process. 

#### ***Area-specific Offshore Scallop results***
```{r offshoreScallop-results, include=FALSE, cache=FALSE}
# clip the data to the Study and Map areas:
osOutputList <- master_intersect(offshoreScallop_rr$data_sf, 
                                              mapDataList, getRegion = TRUE)


# gen table:
if (!is.null(osOutputList$studyData)) {
  osStudyData <- sf::st_drop_geometry(osOutputList$studyData)
  osTable <- osStudyData %>%
  left_join(bankLabels) %>%
  dplyr::select(year, month, name, TOW_NO) %>%
  dplyr::group_by(year, month, name) %>%
  dplyr::summarize(number_of_tows=n()) %>%
  tidyr::pivot_wider(names_from = name, values_from = number_of_tows)
  
  names(osTable)[1]<-"Year"
  names(osTable)[2]<-"Month"
}


```

```{r offshoreScallop-check, echo=FALSE, results='asis',}
# Check if there is any data in the study area
offshoreScallopReport <- if (is.null(osOutputList$studyData)) {
  "* There are no relevant offshoreScallop records for this search area."
} else {
  "* There are relevant offshoreScallop records for this search area."
}
writeLines(noquote(offshoreScallopReport))
```

```{r offshoreScallop-region-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(offshoreScallop_rr, "EN"), 'Map showing location of Offshore Scallop survey stations in the region.')}
if (!is.null(osOutputList$regionData)) {
  # common plotting function:
  plot_rr_sf(regionMap, osOutputList$regionData, attribute = 
               offshoreScallop_rr$attribute, labelData = bankLabels,
             labelAttribute = "name")
}
```

```{r offshoreScallop-area-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(offshoreScallop_rr, "EN"), 'Map showing the search area defined by the user (red outline) used to query information and the location of Offshore Scallop survey stations.')}
if (!is.null(osOutputList$studyData)) {
  
  labelData <- dplyr::filter(bankLabels, bank %in% osOutputList$mapData$bank)
  # common plotting function:
  plot_rr_sf(areaMap, osOutputList$mapData, attribute = 
               offshoreScallop_rr$attribute, labelData = labelData, 
             labelAttribute = "name")
}
```
<br>
```{r offshoreScallop-table}
if (!is.null(osOutputList$studyData)) {
  if (nrow(osTable) > 0) {
     options(knitr.kable.NA = '--')
    knitr::kable(osTable, align = "l", caption = paste("\\label{tab:offshoreScallop_table}", write_caption_blurb(offshoreScallop_rr, "EN"), "Number of tows per year by bank from Offshore Scallop surveys. Icelandic scallop data was collected on Banquereau in 2006, 2012 and 2019 The absence of a record in this table should be interpreted as an absence of reporting, not necessarily as an absence of the species in the area. </b>"), booktabs = T, escape = F, linesep = "") %>% kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
  }
}
```
### Additional information: 

[Stock Status Update of Georges Bank ‘a’ Scallops (Placopecten magellanicus) for the 2020 Fishing Season](https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2020/2020_043-eng.html)

[Assessment of Georges Bank Scallops (Placopecten magellanicus)](https://www.dfo-mpo.gc.ca/csas-sccs/Publications/SAR-AS/2013/2013_058-eng.html)

[Stock Status Update of Browns Bank North Scallops (Placopecten magellanicus) for the 2020 Fishing Season](https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2020/2020_042-eng.html)

[Assessment of Browns Bank North Scallops (Placopecten magellanicus)](https://www.dfo-mpo.gc.ca/csas-sccs/Publications/SAR-AS/2013/2013_059-eng.html)
