---
output: 
  bookdown::html_document2:
    number_sections: FALSE
    theme: paper
bibliography: '`r here::here("app/data/mybiblio.bib")`'
---

```{r offshoreScallop-load-common, child = here::here("reports/sections/commonSections/commonIntro.Rmd")}
```

```{r eval=FALSE}
if (FALSE) { 
  # load in generic data, e.g.functions, study area, and base maps into the 
  # environment, when knitting, these will be loaded through the child rmd.
  lapply(list.files(here::here("reports/R"), pattern = ".[Rr]$", full.names = TRUE), source)
  studyArea <- sf::st_read(here::here("app/output/geoms_slc.geojson"))
  intro_setup(studyArea, env = environment())
}
```

### **Offshore Scallop** {#offshore-scallop-section}

```{r offshoreScallop-load, include=FALSE}
# load in section specific data
load_rdata(c("offshoreScallop_rr"), regionStr, env = environment())

```

```{r offshoreScallop-meta, results='asis'}
# metadata blurb at start of each section
write_meta(offshoreScallop_rr, "EN")
```

The Offshore Scallop Survey Database (SCALOFF) contains data collected through Collaborative Agreements (formerly Joint Project Agreements) between DFO Science and the Seafood Producers Association of Nova Scotia (SPANS). The Offshore Scallop Survey collects data on the stocks of Sea Scallop (*Placopecten magellanicus*) on the Scotian Shelf and the Canadian side of Georges Bank, as well as Iceland Scallop (*Chlamys islandica*) on Banquereau Bank. These stocks correspond to the DFO management units known as Scallop Fishing Areas (SFA) 25, 26, and 27, and the survey data are the primary source of fishery-independent information used in the Maritimes Region scallop stock assessments.

The Offshore Scallop Survey has occurred between May and September annually since 1978 with few exceptions, but spatial coverage and survey designs have changed over time. Regardless of survey design, the same sampling protocol is followed: At each survey station, the 8-ft scallop dredge lined with 38 mm mesh is towed for 10 minutes, and every scallop is counted and assigned to a 5 mm shell height bin (ranging from 0-200 mm). Detailed sampling occurs at a selection of the stations, where the exact shell heights and meat weights are measured for a sub-sample of the scallops caught. Bottom temperature data has also been collected on the Offshore Scallop survey since 2011.  

Under the Collaborative Agreement, survey responsibilities are shared by DFO and SPANS. At-sea survey activities are directed by the DFO Chief Scientist aboard the survey vessel. SPANS coordinates the provision the survey vessel as well as the necessary crew complement to conduct the survey activities. DFO Science designs the survey, provides and manages scientific equipment, and validates, archives, and analyzes survey data. 


Data requests are subject to the terms of the Collaborative Agreement. Please contact Freya Keyser (DFO Offshore Scallop Biologist, freya.keyser@dfo-mpo.gc.ca) with details on your request, and you will be guided through the Offshore Scallop Survey data request process. 

#### *Area-specific Offshore Scallop results*
```{r offshoreScallop-results, include=FALSE, cache=FALSE}
# clip the data to the Study and Map areas:
osOutputList <- master_intersect(offshoreScallop_rr$data_sf, 
                                              mapDataList, getRegion = TRUE)


# gen table:
if (!is.null(osOutputList$studyData)) {
  osStudyData <- sf::st_drop_geometry(osOutputList$studyData)
  osTable <- osStudyData %>%
    left_join(bankLabels) %>%
    dplyr::select(year, name, TOW_NO) %>%
    dplyr::group_by(year, name) %>%
    dplyr::summarize(number_of_tows = n()) %>%
    tidyr::pivot_wider(names_from = name, values_from = number_of_tows)
  
  names(osTable)[1] <- "Year"
 
}


```

```{r offshoreScallop-check, echo=FALSE, results='asis',}
# Check if there is any data in the study area
offshoreScallopReport <- if (is.null(osOutputList$studyData)) {
  "* There are no relevant Offshore Scallop records for this search area."
} else {
  "* There are relevant Offshore Scallop records for this search area."
}
writeLines(noquote(offshoreScallopReport))
```

```{r offshoreScallop-region-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(offshoreScallop_rr, "EN"), 'Map showing the study area’s location relative to the DFO Maritimes Region. Dashed grey line indicates international boundaries.')}
if (!is.null(osOutputList$regionData)) {
  # common plotting function:
  plot_rr_sf(regionMap, osOutputList$regionData, attribute = 
               offshoreScallop_rr$attribute, labelData = bankLabels,
             labelAttribute = "name")
}
```

```{r offshoreScallop-area-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(offshoreScallop_rr, "EN"), 'Map showing the search area defined by the user (red outline) to query information and automatically generate this report.')}
if (!is.null(osOutputList$studyData)) {
  
  labelData <- dplyr::filter(bankLabels, bank %in% osOutputList$mapData$bank)
  # common plotting function:
  plot_rr_sf(areaMap, osOutputList$mapData, attribute = 
               offshoreScallop_rr$attribute, labelData = labelData, 
             labelAttribute = "name")
}
```
<br>
```{r offshoreScallop-table}
if (!is.null(osOutputList$studyData)) {
  if (nrow(osTable) > 0) {
     options(knitr.kable.NA = '--')
    knitr::kable(osTable, align = "l", caption = paste("\\label{tab:offshoreScallop_table}", write_caption_blurb(offshoreScallop_rr, "EN"), 'Spatial and temporal coverage of the Offshore Scallop survey, represented as number of tows per year by bank for the user-defined area (red outline). The absence of a record in this table should be interpreted as an absence of reporting, not necessarily as an absence of the species in the area. Icelandic scallop data were collected on Banquereau in 2006, 2012 and 2019.'), booktabs = T, escape = F, linesep = "") %>% kable_styling(bootstrap_options = "striped", full_width = T, position = "center")
  }
}
```
### Additional information: 
[Offshore Scallop Integrated Fisheries Management Plan - Maritimes Region](https://www.dfo-mpo.gc.ca/fisheries-peches/ifmp-gmp/scallop-petoncle/2018/index-eng.html)

[DFO. 2020 Stock Status Update of Georges Bank 'a' Scallops (*Placopecten magellanicus*) for the 2020 Fishing Season. DFO Can. Sci. Advis. Resp. 2020/43)](https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2020/2020_043-eng.html)

[DFO. 2013. Assessment of Georges Bank Scallops (*Placopecten magellanicus*). DFO Can. Sci. Advis. Sec. Sci. Advis. Rep. 2013/058.](https://www.dfo-mpo.gc.ca/csas-sccs/Publications/SAR-AS/2013/2013_058-eng.html)

[DFO. 2020. Stock Status Update of Browns Bank North Scallops (Placopecten magellanicus) for the 2020 Fishing Season. DFO Can. Sci. Advis. Sec. Sci. Resp. 2020/042.](https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2020/2020_042-eng.html)

[ 2013. Assessment of Browns Bank North Scallops (Placopecten magellanicus). DFO Can. Sci. Advis. Sec. Sci. Advis. Rep. 2013/059.](https://www.dfo-mpo.gc.ca/csas-sccs/Publications/SAR-AS/2013/2013_059-eng.html)
