
---
output:
  bookdown::html_document2:
    number_sections: FALSE
    theme: paper
bibliography: '`r here::here("app/data/mybiblio.bib")`'
---
```{r child = here::here("sections/commonSections/commonIntro.Rmd")}
if (FALSE) { #load in data:
  lapply(list.files(here::here("app/R"), pattern = ".[Rr]$", full.names = TRUE), source)
  studyArea <- sf::st_read(here::here("app/output/geoms_slc.geojson")) 
  intro_setup(studyArea, env = environment())  
}
```

### **Industry Survey and Maritimes Fishery Databases**  

#### ***Industry Survey Database (ISDB)*** {#ISDB-section}

```{r isdb-load, include=FALSE}
load_rdata(c("isdb_rr"), "MAR", env = environment())
```

```{r isdb-meta, results='asis'}
write_meta(isdb_rr, "EN")
```

The Industry Survey Database (ISDB) is a departmental database containing at-sea fish catch observations from commercial fishing vessels operating in the Northwest Atlantic. Records can be associated with regular commercial fishing activities, or can represent industry-led scientific surveys. Industry surveys are not spatially or temporally synoptic and, therefore, integrating additional information on presence and/or habitat use (i.e., spawning, migration, feeding areas) from larger-scale studies is strongly recommended. Fisheries catch and effort information for an individual license holder is considered personal information and is protected under section 19 of the Access to Information Act (https://laws-lois.justice.gc.ca/eng/acts/a-1/page-5.html#h-12), and, for a corporate license holder, is considered to be sensitive, proprietary information and protected under Section 20 of the Access to Information Act (https://laws-lois.justice.gc.ca/eng/acts/a-1/page-5.html#h-13).

Without written consent, DFO is not permitted to release information or data products from ISDB (e.g., maps and data layers) that might reveal personal or third party information such as catch, landed values, and vessel-specific fishing locations, as this information is considered confidential. Information on privacy policy is available in the DFO staff informal release guidelines (i.e., Appendix B – “Catch and Effort and Quota Information: Do’s and Don’ts for Informal Release” (\\\\ent.dfo-mpo.ca\\ATLShares\\Shared\\ATIP Information\\Information_Release_Guidelines-eng.docx). If you are interested in including observer data in a publication, please remember to aggregate it (https://github.com/Maritimes/Mar.utils/blob/master/R/assess_privacy.r).

#### ***The Maritime Fishery Information System (MARFIS)***{#MARFIS-section}

```{r marfis-load, include=FALSE}
load_rdata(c("marfis_rr"), "MAR", env = environment())
```

```{r marfis-meta, results='asis'}
write_meta(marfis_rr, "EN")
```

The Maritimes Fishery Information System (MARFIS) is a DFO database, managed by the Policy & Economics Branch. MARFIS contains catch and effort, quota, and licensing information for the Maritimes Region. Log information for all commercial fisheries that land within this region is associated with this data. If a Maritimes Region commercial vessel makes landings in another DFO region or outside of Canadian waters, information is not included in the MARFIS database, irrespective of whether that vessel originated in Maritimes Region. The majority of catch information is related to commercial offloads i.e. dockside monitoring programs. Reported information contained within MARFIS is not considered spatially or temporally synoptic and, therefore, integrating additional information on presence and/or habitat use (i.e., spawning, migration, feeding) from larger-scale studies is strongly recommended. There is also more limited data related to discards and the Species At Risk data logs. Not all catch records have associated lat/lon coordinates or information on fishing effort. However, generally all records are associated with a NAFO Division and NAFO Unit Area, even if no coordinates have been provided. Production data (<4 years old) are considered preliminary and subject to change without notice. Changes to archived data (>4 years old) may also occur but are generally limited. Ongoing QA/QC work is done on the MARFIS database, but not all errors are corrected. If you have data errors, questions, or corrections, you can send them to our data quality inbox: CDDDataQuality@dfo-mpo.gc.ca. This information about MARFIS was provided by Colin.O'Neil@dfo-mpo.gc.ca (July 2020, Policy & Economics Branch). If you are interested in including comercial catch data in a publication, please remember to aggregate it (https://github.com/Maritimes/Mar.utils/blob/master/R/assess_privacy.r).

#### ***Area-specific MARFIS & ISDB search results***

```{r marfis-isdb-results, include=FALSE, cache=FALSE}
outputListI <- master_intersect(isdb_rr$data_sf, mapDataList, Year = minYear)
outputListM <- master_intersect(marfis_rr$data_sf, mapDataList, Year = minYear)

tableList <- create_table_ISDB(outputListI$studyData, listed_species,
                               speciesTable = ISSPECIESCODES)
isdbAllTable <- tableList$allSpeciesData
isdbSarTable <- tableList$sarData
summarySarTable <- add_col_to_sar_summary(summarySarTable, "[ISDB](#ISDB-section)", isdbSarTable, "Common Name", "Records")

tableList <- create_table_MARFIS(outputListM$studyData, listed_species, speciesTable = MARFISSPECIESCODES)
marfisAllTable <- tableList$allSpeciesData
marfisSarTable <- tableList$sarData
summarySarTable <- add_col_to_sar_summary(summarySarTable, "[MARFIS](#MARFIS-section)", marfisSarTable, "Common Name", "Records")
```
*
```{r isdb-check, comment="", prompt=TRUE, echo=FALSE, results='asis'}
Report_isdb <- if (is.null(outputListI$studyData)) {
    "There are no relevant records in the Industry Survey Database (ISDB) for this search area."
  } else {
    "There are relevant records in the Industry Survey Database (ISDB) for this search area."
  }
Report_isdb <- noquote(Report_isdb)
writeLines(Report_isdb)
```

*
```{r marfis-check, comment="", prompt=TRUE, echo=FALSE, results='asis'}
Report_marfis <- if (is.null(outputListM$studyData)) {
    "There are no relevant records in the Maritimes Fishery Information System (MARFIS) for this search area."
  } else {
    "There are relevant records in the Maritimes Fishery Information System (MARFIS) for this search area."
  }
Report_marfis<-noquote(Report_marfis)
writeLines(Report_marfis)
```

```{r marfis-isdb-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(marfis_rr, "EN"), 'Map showing the search area defined by the user (red outline) used to query aggregated information from Maritimes Fishery Information System (MARFIS) and/or Industry Survey Database (ISDB) observation records shown as black points, for all species. Rule of five was not applied.')}
if (!is.null(outputListI$studyData) & !is.null(outputListM$studyData)) {
  areaMap + geom_point(data = outputListI$mapPoints, aes(x = long, y = lat), size = 2, shape = 16, col = "black") + geom_point(data = outputListM$mapPoints, aes(x = long, y = lat), size = 2, shape = 16, col = "black")
} else if (!is.null(outputListI$studyData)) {
    areaMap + geom_point(data = outputListI$mapPoints, aes(x = long, y = lat), size = 2, shape = 16, col = "black")
} else if (!is.null(outputListM$studyData)) {
        areaMap + geom_point(data = outputListM$mapPoints, aes(x = long, y = lat), size = 2, shape = 16, col = "black")
}
```
```{r isdb-SAR-table}
if (!is.null(outputListI$studyData)) {
knitr::kable(isdbSarTable, align="l", caption=paste(write_caption_blurb(isdb_rr, "EN"), "Industry Survey Database (ISDB) records of species observed within the search area and listed by the <i>Species at Risk Act</i> (SARA), or assessed by the Committee on the Status of Endangered Wildlife in Canada (COSEWIC). <b>The absence of a species in this table should be interpreted as an absence of reporting, not necessarily as an absence of the species in the area.</b>"), booktabs = T, escape = F, linesep="")} %>% kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
<br><br>
```{r isdb-all-table}
if (!is.null(outputListI$studyData)) {
  knitr::kable(isdbAllTable, align="l", caption=paste(write_caption_blurb(isdb_rr, "EN"), "Industry Survey Database (ISDB) records of <u>all species</u> observed within the search area, summarized by species or species group. Records do not necessarily correspond to number of individuals. <b>The absence of a species in this table should be interpreted as an absence of reporting, not necessarily as an absence of the species in the area.</b>"), booktabs = T, escape = F, linesep="")} %>% kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

```{r marfis-SAR-table}
if (!is.null(outputListM$studyData)) {
  knitr::kable(marfisSarTable, align="l", caption=paste(write_caption_blurb(marfis_rr, "EN"), "Maritimes Fishery Information System (MARFIS) records of species observed within the search area and listed by the <i>Species At Risk Act</i> (SARA), or assessed by the Committee on the Status of Endangered Wildlife in Canada (COSEWIC). <b>The absence of a species in this table should be interpreted as an absence of reporting, not necessarily as an absence of the species in the area.</b>"), booktabs = T, escape = F, linesep="")} %>% kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
<br><br>
```{r marfis-all-table}
if (!is.null(outputListM$studyData)) {
  knitr::kable(marfisAllTable, caption=paste(write_caption_blurb(marfis_rr, "EN"), "Maritimes Fishery Information System (MARFIS) records of <u>all species</u> observed within the search area, summarized by species or species group. <b>The absence of a species in this table should be interpreted as an absence of reporting, not necessarily as an absence of the species in the area.</b>"), booktabs = T, escape = F, linesep="")  %>% column_spec(1, width="15cm")
} %>% kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
