---
output:
  bookdown::html_document2:
    number_sections: FALSE
    theme: paper
bibliography: '`r here::here("app/data/mybiblio.bib")`'
---

```{r isleMadame-load-common, child = here::here("reports/sections/commonSections/commonIntro.Rmd")}
```

```{r eval=FALSE}
if (FALSE) { 
  # load in generic data, e.g.functions, study area, and base maps into the 
  # environment, when knitting, these will be loaded through the child rmd.
  lapply(list.files(here::here("reports/R"), pattern = ".[Rr]$", full.names = TRUE), source)
  studyArea <- sf::st_read(here::here("app/output/geoms_slc.geojson"))
  intro_setup(studyArea, env = environment())
}
```

```{r ilseMadame-load, include=FALSE}
# load in generic IM data to make region plots:
load_rdata(c("narWhale_rr"), regionStr, env = environment())

```

### **Species presence polygons within the Bay of Fundy and Port Hawkesbury Response Plan areas** {#speciesPresence-section}

Species presence polygons created by the Integrated Marine Response Planning (IMRP) team (formerly Planning for Integrated Environmental Response, PIER). Presence polygons in this section were derived from various sources of information to determine areas where species are seasonally present within the [Bay of Fundy and Port Hawkesbury Area Response Plan areas](#opprrpe-section). For more information about how these polygons were created, please contact Adrian Hamer (<Adrian.Hamer@dfo-mpo.gc.ca>).

#### *Area-specific Species Presence results*
```{r isleMadame-results, include=FALSE, cache=FALSE}
# clip the data to the Study and Map areas:
outputList <- master_intersect(narWhale_rr$data_sf, mapDataList, getRegion = TRUE)

```

```{r isleMadame-check, echo=FALSE, results='asis',}
# Check if there is any data in the study area
outputReport <- if (is.null(outputList$studyData)) {
  paste("* There are no relevant species presence polygons for this search area within the Bay of Fundy and Port Hawkesbury Response Plan areas.")
} else {
  paste("* There are relevant species presence polygons for this search area within the Bay of Fundy and Port Hawkesbury Response Plan areas.")
}
writeLines(noquote(outputReport))
```

```{r isleMadame-region-plot, fig.height=7, fig.width=11, fig.cap=paste(write_caption_blurb(narWhale_rr, "EN"), 'Map showing the search area defined by the user (red outline) and areas containing species presence data.')}
if (!is.null(outputList$regionData)) {
  plot_rr_sf(regionMap, outputList$regionData, attribute = 
               "NONE")
}
```


```{r isleMadame-introcheck-setup,  include=FALSE}
  imCheck <- FALSE
```

```{r bnWhale-load-section, child = here::here("reports/sections/isleMadame/presence_sections/bnWhale_en.rmd")}
```

```{r fbWhale-load-section, child = here::here("reports/sections/isleMadame/presence_sections/fbWhale_en.rmd")}
```

```{r greySeal-load-section, child = here::here("reports/sections/isleMadame/presence_sections/greySeal_en.rmd")}
```

```{r harbourPorpoise-load-section, child = here::here("reports/sections/isleMadame/presence_sections/harbourPorpoise_en.rmd")}
```

```{r imSalmon-load-section, child = here::here("reports/sections/isleMadame/presence_sections/imSalmon_en.rmd")}
```

```{r imSalmonRivers-load-section, child = here::here("reports/sections/isleMadame/presence_sections/imSalmonRivers_en.rmd")}
```

```{r lobster-load-section, child = here::here("reports/sections/isleMadame/presence_sections/lobster_en.rmd")}
```

```{r narWhale-load-section, child = here::here("reports/sections/isleMadame/presence_sections/narWhale_en.rmd")}
```

```{r snowCrab-load-section, child = here::here("reports/sections/isleMadame/presence_sections/snowcrab_en.rmd")}
```

```{r ssClam-load-section, child = here::here("reports/sections/isleMadame/presence_sections/ssClam_en.rmd")}
```

```{r tuna-load-section, child = here::here("reports/sections/isleMadame/presence_sections/tuna_en.rmd")}
```


```{r isleMadame-intro-check,  include=FALSE}
  summaryIntroTable <- add_row_to_intro_summary(summaryIntroTable, name="[IMRP Species Presence](#speciesPresence-section)", result=imCheck)
```

