---
output:
  bookdown::html_document2:
    number_sections: FALSE
    theme: paper
bibliography: '`r here::here("app/data/mybiblio.bib")`'
---

```{r threats-load-common, child = here::here("reports/sections/commonSections/commonIntro.Rmd")}
``` 

```{r threats-load, include=FALSE}
load_rdata(c("threats_rr"), regionStr, env = environment())
``` 
 
This section of the Report represents a literature review conducted by Stephen Finnis in December 2021 in an attempt to compile and summarize the available threat and mitigation information for aquatic species at risk within the DFO Maritimes region. Together, threats and threat mitigation are important for aiding species recovery, and are addressed at various stages in the SARA recovery planning process, the multi-step approach for providing legal protection for species at risk. This process is complex, and many challenges arise when attempting to compile this information in a standardized manner that is comparable for all species. This section therefore summarizes the recovery planning process and provides an overview of the various parties involved, steps, and documents created, with an emphasis on threats and threat mitigation. In addition, the documents created by DFO within this process are compiled in this section for each aquatic species at risk (i.e., those assessed by the Committee on the Status of Endangered Wildlife in Canada and/or listed within the Species at Risk Act) observed within the search area.  

Click [here](#threats-results-supplementary) for more information about the SARA recovery planning process, which is is fundamental to the work of this section. 

#### *SARA Recovery Planning Process documents* {#threats-results}

```{r cosewic-table, echo = FALSE, results = "asis"}
options(knitr.kable.NA = "")
knitr::kable(nonScheduleOne, align = "l", caption = "Documents containing threat and threat mitigation information for aquatic species within the DFO Maritimes region and surrounding area that have been assessed by the Committee on the Status of Endangered Wildlife in Canada (COSEWIC) but are not currently listed in Schedule 1. Some species may have several COSEWIC populations, which may trigger the creation of a separate series of documents for each population. In many of the datasets in this Report, the COSEWIC population may not be known. Instead, documents have been compiled for all COSEWIC populations within the Maritimes region and surrounding area. Readers of the Report should use their best judgment to determine which set of documents may be the most applicable based on the search area. Blank entries in the Table may be present for various reasons. For example, the document may still in progress but not yet published, or was not created due to a lack of resources. In addition, some documents may not be required based on the COSEWIC designation. RPAs are typically not created for species with a COSEWIC status of special concern. In general, only species that have been included in Schedule 1 will have Action Plans. However, multi-species Action Plans have been created by Parks Canada Agency for several National Parks or National Historic Sites and are included in the Table, if they are available on the species’ SAR Public Registry. RPA Research Documents may only be available in French for several species found within the Quebec region. The documents and species listed in this table are current as of December 2021. New documents or changes in listings may take place as the recovery planning process progresses.", booktabs = T, escape = F, linesep="") %>% kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

```{r sara-table, echo = FALSE, results = "asis"}
knitr::kable(scheduleOne, align = "l", caption = "Documents containing threat and threat mitigation information for aquatic species within the DFO Maritimes region and surrounding area that are listed in Schedule 1. Documents included are those formally required by DFO as part of the SARA recovery planning process are provided. Threat Assessment documents are provided in separate tables. Some species may have several COSEWIC populations, which may trigger the creation of a separate series of documents for each population. In many of the datasets in this Report, the COSEWIC population may not be known. Instead, documents have been compiled for all COSEWIC populations within the Maritimes region and surrounding area. Readers of the Report should use their best judgment to determine which set of documents may be the most applicable based on the search area. Blank entries in the table may be present for various reasons, for example, the document may still in progress but not yet published, or was not created due to a lack of resources. In addition, some documents may not be required based on the COSEWIC designation. RPAs are typically not created for species with a COSEWIC status of special concern. Recovery Strategies and Action Plans are created for species with a SARA designation of threatened, extirpated or endangered, while Management Plans are instead created for species with a SARA designation of special concern. RPA Research Documents may only be available in French for several species found within the Quebec region. The documents and species listed in this table are current as of December 2021. New documents or changes in listings may take place as the recovery planning process progresses.", booktabs = T, escape = F, linesep="") %>% kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

The most detailed information regarding species threats are found within Threat Assessments. These are documents produced by DFO to characterize and prioritize threats in a nationally consistent and standardized manner. Guidelines for creating detailed information on producing Threat Assessments were developed in 2014 and can be found here [@DFO2014_Threat]: <https://waves-vagues.dfo-mpo.gc.ca/Library/363987.pdf>. There are three available Threat assessment documents for Schedule 1 species in the Maritimes region. 

Please refer to the DFO (2014) guidelines for conducting Threat Assessments for detailed descriptions and explanations of each column and the classification scheme for possible entries in each cell: <https://waves-vagues.dfo-mpo.gc.ca/Library/363987.pdf>

The Threat Assessment documents for each species are also provided in the Table captions. Users of the Report should refer to each species document for a full explanation of each table.

```{r mudpiddock-table, echo = FALSE, results = "asis"}
knitr::kable(mudPiddockTable, align = "l", caption = "Threat assessment summary for Atlantic Mud-piddock (*Barnea truncata*) in Canadian waters based on DFO 2014 guidance (obtained from p. 12 in https://waves-vagues.dfo-mpo.gc.ca/Library/40868308.pdf", booktabs = T, escape = F, linesep="") %>% kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

```{r leatherback-table, echo = FALSE, results = "asis"}
knitr::kable(leatherbackTable, align = "l", caption = "Threat assessment for Leatherback Sea Turtles (*Dermochlys coriacea*) in the Broader Northwest Atlantic Population and in Atlantic Canadian waters based on DFO (2014) guidance (obtained from pp. 10-11 in https://waves-vagues.dfo-mpo.gc.ca/Library/40949497.pdf). Numbers in round brackets refer to Notes specified below the Table.", booktabs = T, escape = F, linesep="") %>% kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
#### *Notes*

- Threat risk is unknown because there have been no records of interaction in these fisheries.
- Fishing might not be happening all the time, but these fisheries are open year-round so, as a precautionary approach, the frequency is considered continuous.
- Vertical lines from fixed pots/traps/barrels.
</span>

```{r loggerhead-table, echo = FALSE, results = "asis"}
knitr::kable(loggerheadTable, align = "l", caption = "Threat assessment for the Loggerhead Sea Turtle (*Caretta caretta*) in the Broader Northwest Atlantic Population and in Atlantic Canadian waters based on DFO 2014a guidance (the last three rows represent threats that occur only outside of Canada. Obtained from p. 11 in https://waves-vagues.dfo-mpo.gc.ca/Library/40624201.pdf) Numbers in round brackets refer to Notes specified below the Table.", booktabs = T, escape = F, linesep="") %>% kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

- In Atlantic Canada, the only recorded incidental mortalities of Loggerhead Sea Turtle are attributed to the pelagic longline fishery targeting swordfish and tropical tunas (DFO 2010a). Comparatively in the US, gear types targeting a variety of species are known to cause incidental mortality to Loggerhead Sea Turtles including: bottom trawls, dredges, pelagic longlines, demersal longlines, gillnets and other gear types (NMFS-USFWS 2008a). 
- Entanglement caused by ghost fishing or marine debris is included here. Entanglement in active fishing gear is included in “bycatch”. 
- Marine pollution includes contaminants that Loggerhead Sea Turtles may be exposed to (including from oil pollution) and debris ingestion. 
- Coastal development also includes beach use (e.g., driving on beaches, human presence on beaches in general). 
- Annual mortality at all life stages determined by NMFS-USFWS (2008a) and equated to annual mortalities of nesting females. The NMFS-USFWS (2008a) Relative Reproductive Value (RRV) for oceanic juveniles was used to determine the equivalency of juvenile mortalities bycaught in Atlantic Canada to nesting females. RRVs for each life stage are presented in Table A1-5 in NMFS-USFWS (2008a). For example, a nesting female has an RRV of 1.0 and an oceanic juvenile has an RRV of 0.02 (i.e., one nesting female equates to 34.5 oceanic juveniles).

#### *Disclaimers*

- Although all documents included in this section are required to address threats to species at risk, the level of detail may be variable for each species. This may be due to several different reasons. For instance, these documents were created using the best available information at the time, and some biological data may not be known. In addition, the requirements of several documents have changed over time. As a result, threat and mitigation information are often provided in various forms (e.g., point form, listed in a single sentence or paragraph, or described in a table). Users should refer to each document to understand how threats and mitigation measures were characterized for each species of interest.
- This section focuses on species for which DFO is the responsible authority (i.e., aquatic species), which includes marine reptiles, mammals, mollusks, and fish. Non-aquatic species are under the authority of the Parks Canada Agency if the species are located on federal lands, or Environment and Climate Change Canada for all others. The contents of this Report therefore reflect the recovery planning process for aquatic species. The recovery planning process for non-aquatic species at risk may have slightly different requirements and procedures.
- The literature review summarized in this section was developed in December 2021, and some information may change over time. For example, new species may get assessed by COSEWIC or listed in Schedule 1, thereby triggering the creation of new documents to fulfill the requirements of the recovery planning process. Our group is currently looking into mechanisms to ensure this information is updated on an annual basis.
- Each species may have distinct populations (referred to as Designatable Units, or DUs, under COSEWIC), and each population may have different COSEWIC and/or SARA statuses. As a result, a different series of documents may be created for each population. However, in many of the datasets within this Report, the population of each species may not be specified. Therefore, the documents for all populations of each species within the Maritimes and surrounded area are provided. Readers of this Report should use their best judgement to determine which set of documents may be the most applicable in their search area. 
- This section of the Report focuses on documents created as part of the SARA recovery planning process. There may be other documents created by DFO that address threats and mitigation measures for the species of interest. Those were not included as they are considered outside the scope of this section of the Report.
- This section of the Report focuses on the ecological and biological significance of threats and mitigation measures for species at risk. However, these topics operate within the Species at Risk Act (2002) and the terms and procedures may therefore be subject to legal or judicial interpretation. Users should refer to the Act for precise definitions and descriptions of processes, if required.
